### 2023-02-26 paper/main.tex
bib does not work

\documentclass{article}
\usepackage{arxiv}

\usepackage[utf8]{inputenc}
\usepackage[english, russian]{babel}
\usepackage[T1]{fontenc}
\usepackage{url}
\usepackage{booktabs}
\usepackage{amsfonts}
\usepackage{nicefrac}
\usepackage{microtype}
\usepackage{lipsum}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{doi}
\usepackage{biblatex}
\addbibresource{references.bib}

\title{Differentiable algorithm for searching ensembles of deep learning models with diversity control}

\author{K. Yakovlev, O.Bakhteev, K. Petrushina, P. Babkin
	%% David S.~Hippocampus\thanks{Use footnote for providing further
	%%	information about author (webpage, alternative
	%%	address)---\emph{not} for acknowledging funding agencies.} \\
	%%Department of Computer Science\\
	%%Cranberry-Lemon University\\
	%%Pittsburgh, PA 15213 \\
	%%\texttt{hippo@cs.cranberry-lemon.edu} \\
	%% examples of more authors
	%%\And
	%%Elias D.~Striatum \\
	%%Department of Electrical Engineering\\
	%%Mount-Sheikh University\\
	%%Santa Narimana, Levand \\
	%%\texttt{stariate@ee.mount-sheikh.edu} \\
	%% \AND
	%% Coauthor \\
	%% Affiliation \\
	%% Address \\
	%% \texttt{email} \\
	%% \And
	%% Coauthor \\
	%% Affiliation \\
	%% Address \\
	%% \texttt{email} \\
	%% \And
	%% Coauthor \\
	%% Affiliation \\
	%% Address \\
	%% \texttt{email} \\
}
\date{}

\renewcommand{\shorttitle}{differentiable ensembles search}

%%% Add PDF metadata to help others organize their library
%%% Once the PDF is generated, you can check the metadata with
%%% $ pdfinfo template.pdf
\hypersetup{
pdftitle={Differentiable algorithm for searching ensembles of deep learning models with diversity control},
pdfsubject={q-bio.NC, q-bio.QM},
pdfauthor={K. Yakovlev, O.Bakhteev, K. Petrushina, P. Babkin},
pdfkeywords={First keyword, Second keyword, More},
}

\begin{document}
\maketitle

\begin{abstract}

This paper is developed to introduce a new method of creating ensembles of deep learning models. 
Many modern researches were focused on creating effective and efficient algorithms of differentiable architecture search,
missing oppotunity to create ensembles of deep learning models. This approach gives impressive results
as it was shown in few modern papers. In our research we investigate an algorithm of sampling deep learning models using
hypernetwork, which controls diversity of the models. This method allows us to sample deep learning models in one-shot,
withiout any additional calculational losses, this independence means that algorithm is able to sample as many models
as we want. To evaluate the performance of the proposed algorithm, we conducted experiments on the Fashion-MNIST and CIFAR-10
datasets and compare the resulting ensembles with ones sampled by other searching algorithms.

\end{abstract}

\keywords{ differential search \and neural emsembles \and hypernetwork \and diversity control }

\section{Introduction}

Nowadays algorithms of neural architecture search (NAS) are well-explored and prooved to be an effective way of creating
more effective and efficient neural networks. Such algorithms use different ways to make problem diffirentiable so it can
be solved by wide range of methods for smooth optimization problems. On the other hand, neural ensemble search (NES) is
modern and not as well investigated problem as NAS, although it is known that ensembles of deep learning models show better
results in different applied problems.

Our paper investigates an algorithm of sampling deep learning models in a new way. Despite the fact that similar algorithms
were discribed and investigated, our scheme has uniqeue set of techniques that gives compatible results and has its own sphere
of implimentations.

First of all, we use DARTS as our basic NAS algorithm. It is prooved to be an effective architecture search algorithm. Some
modern investigations have shown that the algorithm can be upgrated, but the modernisations do not make tangible difference
and are mainly made for some specific cases. So in our paper we are focusing on ensemble sampling, so slightly different base
model does not change anything in resulting ensemble.

Second of all, we use hypernetwork in our sampling algorithm. Hypernetwork is small network so it does not
consume too much computational capacity. This network contains information about another network, which is called target network.
This approach is not new: hypernetworks and supernetworks were intended to control different characteristics such as
complexity of acrhitecture or parameters of the target model in several modern investigations. In our algorithm it controls 
diversity of the target models, so every sampled model differs from previously sampled ones.

The hypernetwork uses Jensen-Shennon divergence (JSd) to measure difference between two architectures which is simmetric and finite
in contrast to more popular Kullback–Leibler divergence. Our main idea of sampling different model is to use a reguralizer,
based on JSd as a source of diversity.

This way we are able to sample deep learning models in one-shot, without and additional computational losses.
To sum up the scheme of our method:
\begin{enumerate} 
    \item find a base architectire using DARTS
    \item sample architectures in one-shot via differentiable algorithm
    \item inferencing answer is ensemble of the sampled deep learning models
\end{enumerate}

\printbibliography

\end{document}

### 2023-03-07 code/datasets.py
code for base experiment

@@ -1,0 +1,64 @@
+# Copyright (c) Microsoft Corporation.
+# Licensed under the MIT license.
+
+import numpy as np
+import torch
+from torchvision import transforms
+from torchvision.datasets import CIFAR10, FashionMNIST
+
+
+class Cutout(object):
+    def __init__(self, length):
+        self.length = length
+
+    def __call__(self, img):
+        h, w = img.size(1), img.size(2)
+        mask = np.ones((h, w), np.float32)
+        y = np.random.randint(h)
+        x = np.random.randint(w)
+
+        y1 = np.clip(y - self.length // 2, 0, h)
+        y2 = np.clip(y + self.length // 2, 0, h)
+        x1 = np.clip(x - self.length // 2, 0, w)
+        x2 = np.clip(x + self.length // 2, 0, w)
+
+        mask[y1: y2, x1: x2] = 0.
+        mask = torch.from_numpy(mask)
+        mask = mask.expand_as(img)
+        img *= mask
+
+        return img
+
+
+def get_dataset(cls, cutout_length=0):
+    if cls == "cifar10":
+        MEAN = [0.49139968, 0.48215827, 0.44653124]
+        STD = [0.24703233, 0.24348505, 0.26158768]
+    elif cls == "fashionmnist":
+        MEAN = [0.49139968]
+        STD = [0.24703233]
+
+    transf = [
+        transforms.RandomCrop(32, padding=4),
+        transforms.RandomHorizontalFlip()
+    ]
+    normalize = [
+        transforms.ToTensor(),
+        transforms.Normalize(MEAN, STD)
+    ]
+    cutout = []
+    if cutout_length > 0:
+        cutout.append(Cutout(cutout_length))
+
+    train_transform = transforms.Compose(transf + normalize + cutout)
+    valid_transform = transforms.Compose(normalize)
+
+    if cls == "cifar10":
+        dataset_train = CIFAR10(root="./data", train=True, download=True, transform=train_transform)
+        dataset_valid = CIFAR10(root="./data", train=False, download=True, transform=valid_transform)
+    elif cls == "fashionmnist":
+        dataset_train = FashionMNIST(root="./data", train=True, download=True, transform=train_transform)
+        dataset_valid = FashionMNIST(root="./data", train=False, download=True, transform=valid_transform)
+    else:
+        raise NotImplementedError
+    return dataset_train, dataset_valid

### 2023-03-07 code/model.py

@@ -1,0 +1,160 @@
+# Copyright (c) Microsoft Corporation.
+# Licensed under the MIT license.
+
+from collections import OrderedDict
+
+import torch
+import torch.nn as nn
+
+import ops
+from nni.retiarii.nn.pytorch import LayerChoice, InputChoice
+
+
+class AuxiliaryHead(nn.Module):
+    """ Auxiliary head in 2/3 place of network to let the gradient flow well """
+
+    def __init__(self, input_size, C, n_classes):
+        """ assuming input size 7x7 or 8x8 """
+        assert input_size in [7, 8]
+        super().__init__()
+        self.net = nn.Sequential(
+            nn.ReLU(inplace=True),
+            nn.AvgPool2d(5, stride=input_size - 5, padding=0, count_include_pad=False),  # 2x2 out
+            nn.Conv2d(C, 128, kernel_size=1, bias=False),
+            nn.BatchNorm2d(128),
+            nn.ReLU(inplace=True),
+            nn.Conv2d(128, 768, kernel_size=2, bias=False),  # 1x1 out
+            nn.BatchNorm2d(768),
+            nn.ReLU(inplace=True)
+        )
+        self.linear = nn.Linear(768, n_classes)
+
+    def forward(self, x):
+        out = self.net(x)
+        out = out.view(out.size(0), -1)  # flatten
+        logits = self.linear(out)
+        return logits
+
+
+class Node(nn.Module):
+    def __init__(self, node_id, num_prev_nodes, channels, num_downsample_connect):
+        super().__init__()
+        self.ops = nn.ModuleList()
+        choice_keys = []
+        for i in range(num_prev_nodes):
+            stride = 2 if i < num_downsample_connect else 1
+            choice_keys.append("{}_p{}".format(node_id, i))
+            self.ops.append(
+                LayerChoice(OrderedDict([
+                    ("maxpool", ops.PoolBN('max', channels, 3, stride, 1, affine=False)),
+                    ("avgpool", ops.PoolBN('avg', channels, 3, stride, 1, affine=False)),
+                    ("skipconnect", nn.Identity() if stride == 1 else ops.FactorizedReduce(channels, channels, affine=False)),
+                    ("sepconv3x3", ops.SepConv(channels, channels, 3, stride, 1, affine=False)),
+                    ("sepconv5x5", ops.SepConv(channels, channels, 5, stride, 2, affine=False)),
+                    ("dilconv3x3", ops.DilConv(channels, channels, 3, stride, 2, 2, affine=False)),
[…]

### 2023-03-07 code/retrain.py

@@ -1,0 +1,158 @@
+# Copyright (c) Microsoft Corporation.
+# Licensed under the MIT license.
+
+import logging
+import time
+from argparse import ArgumentParser
+
+import torch
+import torch.nn as nn
+from torch.utils.tensorboard import SummaryWriter
+
+import datasets
+import utils
+from model import CNN
+from nni.nas.pytorch.utils import AverageMeter
+from nni.retiarii import fixed_arch
+
+logger = logging.getLogger('nni')
+
+
+device = torch.device("cuda" if torch.cuda.is_available() else "cpu")
+writer = SummaryWriter()
+
+
+def train(config, train_loader, model, optimizer, criterion, epoch):
+    top1 = AverageMeter("top1")
+    top5 = AverageMeter("top5")
+    losses = AverageMeter("losses")
+
+    cur_step = epoch * len(train_loader)
+    cur_lr = optimizer.param_groups[0]["lr"]
+    logger.info("Epoch %d LR %.6f", epoch, cur_lr)
+    writer.add_scalar("lr", cur_lr, global_step=cur_step)
+
+    model.train()
+
+    for step, (x, y) in enumerate(train_loader):
+        x, y = x.to(device, non_blocking=True), y.to(device, non_blocking=True)
+        bs = x.size(0)
+
+        optimizer.zero_grad()
+        logits, aux_logits = model(x)
+        loss = criterion(logits, y)
+        if config.aux_weight > 0.:
+            loss += config.aux_weight * criterion(aux_logits, y)
+        loss.backward()
+        # gradient clipping
+        nn.utils.clip_grad_norm_(model.parameters(), config.grad_clip)
+        optimizer.step()
+
+        accuracy = utils.accuracy(logits, y, topk=(1, 5))
+        losses.update(loss.item(), bs)
+        top1.update(accuracy["acc1"], bs)
+        top5.update(accuracy["acc5"], bs)
+        writer.add_scalar("loss/train", loss.item(), global_step=cur_step)
+        writer.add_scalar("acc1/train", accuracy["acc1"], global_step=cur_step)
+        writer.add_scalar("acc5/train", accuracy["acc5"], global_step=cur_step)
+
+        if step % config.log_frequency == 0 or step == len(train_loader) - 1:
+            logger.info(
+                "Train: [{:3d}/{}] Step {:03d}/{:03d} Loss {losses.avg:.3f} "
[…]

### 2023-03-07 code/search.py

@@ -1,0 +1,80 @@
+# Copyright (c) Microsoft Corporation.
+# Licensed under the MIT license.
+
+import json
+import logging
+import time
+from argparse import ArgumentParser
+
+import torch
+import torch.nn as nn
+
+import datasets
+from model import CNN
+#from nni.nas.pytorch.callbacks import ArchitectureCheckpoint, LRSchedulerCallback
+from utils import accuracy, MyDartsTrainer
+
+
+logger = logging.getLogger('nni')
+dataset = "fashionmnist"
+
+if __name__ == "__main__":
+    parser = ArgumentParser("darts")
+    parser.add_argument("--layers", default=1, type=int)
+    parser.add_argument("--batch-size", default=64, type=int)
+    parser.add_argument("--log-frequency", default=10, type=int)
+    parser.add_argument("--epochs", default=10, type=int)
+    parser.add_argument("--channels", default=16, type=int)
+    parser.add_argument("--unrolled", default=False, action="store_true")
+    parser.add_argument("--visualization", default=False, action="store_true")
+    parser.add_argument("--v1", default=False, action="store_true")
+    args = parser.parse_args()
+
+    dataset_train, dataset_valid = datasets.get_dataset(dataset)
+
+    if dataset == "fashionmnist":
+        model = CNN(32, 1, args.channels, 10, args.layers)
+    if dataset == "cifar10":
+        model = CNN(32, 3, args.channels, 10, args.layers)
+
+    criterion = nn.CrossEntropyLoss() # mycriterion()
+
+    optim = torch.optim.SGD(model.parameters(), 0.025, momentum=0.9, weight_decay=3.0E-4)
+    lr_scheduler = torch.optim.lr_scheduler.CosineAnnealingLR(optim, args.epochs, eta_min=0.001)
+
+    if args.v1:
+        from nni.algorithms.nas.pytorch.darts import DartsTrainer
+        trainer = DartsTrainer(model,
+                               loss=criterion,
+                               metrics=lambda output, target: accuracy(output, target, topk=(1,)),
+                               optimizer=optim,
+                               num_epochs=args.epochs,
+                               dataset_train=dataset_train,
+                               dataset_valid=dataset_valid,
+                               batch_size=args.batch_size,
+                               log_frequency=args.log_frequency,
+                               unrolled=args.unrolled,
+                               callbacks=[LRSchedulerCallback(lr_scheduler), ArchitectureCheckpoint("./checkpoints")])
[…]

### 2023-03-07 code/utils.py

@@ -1,0 +1,82 @@
+# Copyright (c) Microsoft Corporation.
+# Licensed under the MIT license.
+
+def accuracy(output, target, topk=(1,)):
+    """ Computes the precision@k for the specified values of k """
+    maxk = max(topk)
+    batch_size = target.size(0)
+
+    _, pred = output.topk(maxk, 1, True, True)
+    pred = pred.t()
+    # one-hot case
+    if target.ndimension() > 1:
+        target = target.max(1)[1]
+
+    correct = pred.eq(target.view(1, -1).expand_as(pred))
+
+    res = dict()
+    for k in topk:
+        correct_k = correct[:k].reshape(-1).float().sum(0)
+        res["acc{}".format(k)] = correct_k.mul_(1.0 / batch_size).item()
+    return res
+
+#==========================================================================
+
+from nni.retiarii.oneshot.pytorch import DartsTrainer
+import torch.nn.functional as F
+import torch
+import json
+
+def JSD(t1, t2): # tensor, tensor -> float
+    m = 0.5 * (t1 + t2)
+    loss = 0.0
+    loss += F.kl_div(t1, m, reduction="batchmean") 
+    loss += F.kl_div(t1, m, reduction="batchmean") 
+    return (0.5 * loss)
+
+class MyDartsTrainer(DartsTrainer):
+    def __init__(self, model, loss, metrics, optimizer,
+                 num_epochs, dataset, grad_clip=5.,
+                 learning_rate=2.5E-3, batch_size=64, workers=4,
+                 device=None, log_frequency=None,
+                 arc_learning_rate=3.0E-4, unrolled=False, tau=0.95, decay=0):
+        super().__init__(model, loss, metrics, optimizer,
+                 num_epochs, dataset, grad_clip,
+                 learning_rate, batch_size, workers,
+                 device, log_frequency,
+                 arc_learning_rate, unrolled)
+        self.tau = tau
+        self.decay = decay
+        
+        operations = { "maxpool": 0, "avgpool": 1, "skipconnect": 2, "sepconv3x3": 3,
+                      "sepconv5x5": 4, "dilconv3x3" : 5, "dilconv5x5" : 6 } # индексы операций по названиям (в соответствии с nas_modules)
+        O = len(operations) # кол-во операций
+
+        self.optimal = {} # выдает сглаженный тензор операций по названию операции
+        with open('checkpoint_optimum.json') as f:
+            checkpoint_optimum = json.load(f) # оптимальная архитектура в виде словаря
+
[…]

### 2023-03-07 code/search.py
bug fix

@@ -72,7 +72,7 @@ if __name__ == "__main__":
             log_frequency=args.log_frequency,
             unrolled=args.unrolled,
             tau=0.95, # параметр сглаживания для подсчета дивергенции
-            decay=1 # вес регуляризации
+            decay=-1e10 # вес регуляризации
         )
         trainer.fit()
         final_architecture = trainer.export()

### 2023-03-07 code/utils.py

@@ -27,12 +27,19 @@ import torch.nn.functional as F
 import torch
 import json
 
-def JSD(t1, t2): # tensor, tensor -> float
-    m = 0.5 * (t1 + t2)
+
+def JSD(net_1_logits, net_2_logits):
+    from torch.functional import F
+    net_1_probs = F.softmax(net_1_logits, dim=0)
+    net_2_probs = F.softmax(net_2_logits, dim=0)
+    
+    total_m = 0.5 * (net_1_probs + net_2_probs)
+    
     loss = 0.0
-    loss += F.kl_div(t1, m, reduction="batchmean") 
-    loss += F.kl_div(t1, m, reduction="batchmean") 
+    loss += F.kl_div(F.log_softmax(net_1_logits, dim=0), total_m, reduction="batchmean") 
+    loss += F.kl_div(F.log_softmax(net_2_logits, dim=0), total_m, reduction="batchmean") 
     return (0.5 * loss)
+
 
 class MyDartsTrainer(DartsTrainer):
     def __init__(self, model, loss, metrics, optimizer,
@@ -72,11 +79,11 @@ class MyDartsTrainer(DartsTrainer):
         res = 0.0
         for name, module in self.nas_modules: # суммируем диаергенцию по всем ребрам
             if name in self.optimal.keys():
-                res += JSD(F.softmax(module.alpha.data), self.optimal[name])
+                res += JSD(module.alpha.data, self.optimal[name])
         return res
 
     def _logits_and_loss(self, X, y):
         logits = self.model(X)
         loss = self.loss(logits, y) - self.decay * self.JSD() # обращаем внимание, что регуляризатор не влияет на первый уровень оптимизации
-        if loss < 0: loss = 0
+        if loss < 0: loss = 0.01
         return logits, loss

### 2023-03-08 code/utils.py
Fixed JSD calculation, removed extra loss clipping

@@ -77,13 +77,14 @@ class MyDartsTrainer(DartsTrainer):
 
     def JSD(self): # подсчет дивергенции между своей и оптимальной архитектурой
         res = 0.0
+        count = 0
         for name, module in self.nas_modules: # суммируем диаергенцию по всем ребрам
             if name in self.optimal.keys():
-                res += JSD(module.alpha.data, self.optimal[name])
-        return res
+                res += JSD(module.alpha, torch.log(self.optimal[name]))
+                count += 1
+        return res / count
 
     def _logits_and_loss(self, X, y):
         logits = self.model(X)
         loss = self.loss(logits, y) - self.decay * self.JSD() # обращаем внимание, что регуляризатор не влияет на первый уровень оптимизации
-        if loss < 0: loss = 0.01
         return logits, loss

### 2023-03-08 code/retrain.py
Fixed retrain, added arguments for search

@@ -12,7 +12,7 @@ from torch.utils.tensorboard import SummaryWriter
 import datasets
 import utils
 from model import CNN
-from nni.nas.pytorch.utils import AverageMeter
+from nni.retiarii.oneshot.pytorch.utils import AverageMeter
 from nni.retiarii import fixed_arch
 
 logger = logging.getLogger('nni')
@@ -117,10 +117,10 @@ if __name__ == "__main__":
     parser.add_argument("--arc-checkpoint", default="./checkpoints/epoch_0.json")
 
     args = parser.parse_args()
-    dataset_train, dataset_valid = datasets.get_dataset("cifar10", cutout_length=16)
+    dataset_train, dataset_valid = datasets.get_dataset("fashionmnist", cutout_length=16)
 
     with fixed_arch(args.arc_checkpoint):
-        model = CNN(32, 3, 36, 10, args.layers, auxiliary=True)
+        model = CNN(32, 1, 36, 10, args.layers, auxiliary=True)
     criterion = nn.CrossEntropyLoss()
 
     model.to(device)

### 2023-03-08 code/search.py

@@ -11,7 +11,6 @@ import torch.nn as nn
 
 import datasets
 from model import CNN
-#from nni.nas.pytorch.callbacks import ArchitectureCheckpoint, LRSchedulerCallback
 from utils import accuracy, MyDartsTrainer
 
 
@@ -25,9 +24,10 @@ if __name__ == "__main__":
     parser.add_argument("--log-frequency", default=10, type=int)
     parser.add_argument("--epochs", default=10, type=int)
     parser.add_argument("--channels", default=16, type=int)
+    parser.add_argument("--decay", default=0.0, type=float, help='regularization coefficient')
     parser.add_argument("--unrolled", default=False, action="store_true")
     parser.add_argument("--visualization", default=False, action="store_true")
-    parser.add_argument("--v1", default=False, action="store_true")
+    parser.add_argument("--save_path", default='finar_architecture.json', type=str)
     args = parser.parse_args()
 
     dataset_train, dataset_valid = datasets.get_dataset(dataset)
@@ -42,39 +42,20 @@ if __name__ == "__main__":
     optim = torch.optim.SGD(model.parameters(), 0.025, momentum=0.9, weight_decay=3.0E-4)
     lr_scheduler = torch.optim.lr_scheduler.CosineAnnealingLR(optim, args.epochs, eta_min=0.001)
 
-    if args.v1:
-        from nni.algorithms.nas.pytorch.darts import DartsTrainer
-        trainer = DartsTrainer(model,
-                               loss=criterion,
-                               metrics=lambda output, target: accuracy(output, target, topk=(1,)),
-                               optimizer=optim,
-                               num_epochs=args.epochs,
-                               dataset_train=dataset_train,
-                               dataset_valid=dataset_valid,
-                               batch_size=args.batch_size,
-                               log_frequency=args.log_frequency,
-                               unrolled=args.unrolled,
-                               callbacks=[LRSchedulerCallback(lr_scheduler), ArchitectureCheckpoint("./checkpoints")])
-        if args.visualization:
-            trainer.enable_visualization()
-
-        trainer.train()
-    else:
-        from nni.retiarii.oneshot.pytorch import DartsTrainer
-        trainer = MyDartsTrainer( # MyDartsTrainer
-            model=model,
-            loss=criterion, # =mycriterion,
-            metrics=lambda output, target: accuracy(output, target, topk=(1,)),
-            optimizer=optim,
[…]

### 2023-03-13 code/inference.py
inference done + README for run updated

@@ -1,0 +1,86 @@
+# Copyright (c) Microsoft Corporation.
+# Licensed under the MIT license.
+
+import logging
+import time
+from argparse import ArgumentParser
+
+import torch
+import torch.nn as nn
+from torch.utils.tensorboard import SummaryWriter
+
+import datasets
+import utils
+from model import CNN
+from nni.retiarii.oneshot.pytorch.utils import AverageMeter
+from nni.retiarii import fixed_arch
+from glob import glob
+
+logger = logging.getLogger('nni')
+
+
+device = torch.device("cuda" if torch.cuda.is_available() else "cpu")
+writer = SummaryWriter()
+
+
+if __name__ == "__main__":
+    parser = ArgumentParser("darts")
+    parser.add_argument("--layers", default=2, type=int)
+    parser.add_argument("--batch-size", default=96, type=int)
+    parser.add_argument("--log-frequency", default=10, type=int)
+    parser.add_argument("--epochs", default=50, type=int)
+    parser.add_argument("--aux-weight", default=0.4, type=float)
+    parser.add_argument("--drop-path-prob", default=0.1, type=float)
+    parser.add_argument("--workers", default=4)
+    parser.add_argument("--grad-clip", default=5., type=float)
+    parser.add_argument("--checkpoints-folder", default="./checkpoints")
+
+    args = parser.parse_args()
+    dataset_train, dataset_valid = datasets.get_dataset("fashionmnist", cutout_length=16)
+
+    models = []
+    for dir in glob(args.checkpoints_folder + "/*"):
+        print(dir)
+        with fixed_arch(dir + "/arc.json"):
+            model = CNN(32, 1, 36, 10, args.layers, auxiliary=True)
+        model.eval()
+        model.to(device)
+        model.load_state_dict(torch.load(dir + "/mod.json"))
+        
+        models.append(model)
+    print(len(models))
+    valid_loader = torch.utils.data.DataLoader(dataset_valid,
+                                                batch_size=args.batch_size,
+                                                shuffle=False,
+                                                num_workers=args.workers,
+                                                pin_memory=True)
+    criterion = nn.CrossEntropyLoss()
+
+    top1 = AverageMeter("top1")
+    top5 = AverageMeter("top5")
+    losses = AverageMeter("losses")
+
+    # validation
+    for step, (X, y) in enumerate(valid_loader):
[…]

### 2023-03-13 code/retrain.py

@@ -114,12 +114,12 @@ if __name__ == "__main__":
     parser.add_argument("--drop-path-prob", default=0.1, type=float)
     parser.add_argument("--workers", default=4)
     parser.add_argument("--grad-clip", default=5., type=float)
-    parser.add_argument("--arc-checkpoint", default="./checkpoints/epoch_0.json")
+    parser.add_argument("--save-folder", default="./checkpoints/0")
 
     args = parser.parse_args()
     dataset_train, dataset_valid = datasets.get_dataset("fashionmnist", cutout_length=16)
 
-    with fixed_arch(args.arc_checkpoint):
+    with fixed_arch(args.save_folder + "/arc.json"):
         model = CNN(32, 1, 36, 10, args.layers, auxiliary=True)
     criterion = nn.CrossEntropyLoss()
 
@@ -155,4 +155,5 @@ if __name__ == "__main__":
 
         lr_scheduler.step()
 
+    torch.save(model.state_dict(), args.save_folder + "/mod.json")
     logger.info("Final best Prec@1 = {:.4%}".format(best_top1))

### 2023-03-13 code/search.py

@@ -27,7 +27,7 @@ if __name__ == "__main__":
     parser.add_argument("--decay", default=0.0, type=float, help='regularization coefficient')
     parser.add_argument("--unrolled", default=False, action="store_true")
     parser.add_argument("--visualization", default=False, action="store_true")
-    parser.add_argument("--save_path", default='finar_architecture.json', type=str)
+    parser.add_argument("--save-folder", default='checkpoints/0', type=str)
     args = parser.parse_args()
 
     dataset_train, dataset_valid = datasets.get_dataset(dataset)
@@ -58,4 +58,4 @@ if __name__ == "__main__":
     trainer.fit()
     final_architecture = trainer.export()
     print('Final architecture:', trainer.export())
-    json.dump(trainer.export(), open(args.save_path, 'w'))
+    json.dump(trainer.export(), open(args.save_folder + '/arc.json', 'w+'))

### 2023-03-13 code/utils.py

@@ -60,7 +60,7 @@ class MyDartsTrainer(DartsTrainer):
         O = len(operations) # кол-во операций
 
         self.optimal = {} # выдает сглаженный тензор операций по названию операции
-        with open('checkpoint_optimum.json') as f:
+        with open('checkpoints/0/arc.json') as f:
             checkpoint_optimum = json.load(f) # оптимальная архитектура в виде словаря
 
         for name, _ in self.nas_modules:

### 2023-03-18 code/inference.py
logits-mean -> probabilities-mean

@@ -48,7 +48,7 @@ if __name__ == "__main__":
         model.load_state_dict(torch.load(dir + "/mod.json"))
         
         models.append(model)
-    print(len(models))
+
     valid_loader = torch.utils.data.DataLoader(dataset_valid,
                                                 batch_size=args.batch_size,
                                                 shuffle=False,
@@ -61,17 +61,18 @@ if __name__ == "__main__":
     losses = AverageMeter("losses")
 
     # validation
+    softmax = nn.Softmax(dim=1)
     for step, (X, y) in enumerate(valid_loader):
             X, y = X.to(device, non_blocking=True), y.to(device, non_blocking=True)
             bs = X.size(0)
 
-            logits = models[0](X)
+            probabilities = softmax(models[0](X))
             for i in range(1, len(models)):
-                 logits += models[i](X)
-            logits = logits / len(models)
-            loss = criterion(logits, y)
+                 probabilities += softmax(models[i](X))
+            probabilities = probabilities / len(models)
+            loss = criterion(probabilities, y)
 
-            accuracy = utils.accuracy(logits, y, topk=(1, 5))
+            accuracy = utils.accuracy(probabilities, y, topk=(1, 5))
             losses.update(loss.item(), bs)
             top1.update(accuracy["acc1"], bs)
             top5.update(accuracy["acc5"], bs)

### 2023-03-18 paper/main.tex
tex updated

@@
 \usepackage{graphicx}
-\usepackage{natbib}
+\graphicspath{{../figures}}
+\usepackage[square,numbers]{natbib}
+\bibliographystyle{abbrvnat}
+\usepackage{amsmath}
+
 \usepackage{doi}
-\usepackage{biblatex}
-\addbibresource{references.bib}
 
-\title{Differentiable algorithm for searching ensembles of deep learning models with diversity control}
+\title{Differential neural ensemble search with diversity control}
 
@@
 pdfsubject={q-bio.NC, q-bio.QM},
-pdfauthor={K. Yakovlev, O.Bakhteev, K. Petrushina, P. Babkin},
+pdfauthor={P.Babkin, K.Petrushina, K.Yakovlev, O.Bakhteev},
 pdfkeywords={First keyword, Second keyword, More},
@@
 
-This paper is developed to introduce a new method of creating ensembles of deep learning models. 
-Many modern researches were focused on creating effective and efficient algorithms of differentiable architecture search,
-missing oppotunity to create ensembles of deep learning models. This approach gives impressive results
-as it was shown in few modern papers. In our research we investigate an algorithm of sampling deep learning models using
-hypernetwork, which controls diversity of the models. This method allows us to sample deep learning models in one-shot,
-withiout any additional calculational losses, this independence means that algorithm is able to sample as many models
-as we want. To evaluate the performance of the proposed algorithm, we conducted experiments on the Fashion-MNIST and CIFAR-10
+This paper introduces a new method of deep learning ensemble contsruction.
+In our research we investigate an algorithm of sampling the deep learning models using
+hypernetwork.
+Hypernetwork is a neural network which controls diversity of the models.
+It translates a real number into an architecture of a sampled neural network.
+This method samples deep learning models in one-shot regime, without any additional calculations losses.
+To evaluate the performance of the proposed algorithm, we conduct experiments on the Fashion-MNIST and CIFAR-10
 datasets and compare the resulting ensembles with ones sampled by other searching algorithms.
@@
 
-\keywords{ differential search \and neural emsembles \and hypernetwork \and diversity control }
+\keywords{ differential search \and neural ensembles \and hypernetwork \and diversity control }
 
@@
 
-Nowadays algorithms of neural architecture search (NAS) are well-explored and prooved to be an effective way of creating
-more effective and efficient neural networks. Such algorithms use different ways to make problem diffirentiable so it can
-be solved by wide range of methods for smooth optimization problems. On the other hand, neural ensemble search (NES) is
+Nowadays methods of neural architecture search (NAS) are well-explored and proved to be an effective way of creating
+more effective and efficient neural networks \citep{darts, robustify, xnas}. Some of these methods use different ways to smooth out the architecture so optimum for it can
+be found by wide range of methods for smooth optimization problems. On the other hand, neural ensemble search (NES) is
 modern and not as well investigated problem as NAS, although it is known that ensembles of deep learning models show better
-results in different applied problems.
+results in different applied problems \citep{multi-head}.
+Our paper investigates an method of sampling deep learning models in a new way that gives compatible results and has its own sphere
+of implementations.
 
-Our paper investigates an algorithm of sampling deep learning models in a new way. Despite the fact that similar algorithms
-were discribed and investigated, our scheme has uniqeue set of techniques that gives compatible results and has its own sphere
-of implimentations.
+Our method takes the result of NAS as a base architecture than it samples architectures which are close to the optimal one in terms of Jensen-Shennon divergence (JSd).
+Method can control whether sampled architectures are close enough to the optimal one so they give good results on the original dataset and are diverse enough so every architecture makes its own contribution to the final answer.
 
-First of all, we use DARTS as our basic NAS algorithm. It is prooved to be an effective architecture search algorithm. Some
-modern investigations have shown that the algorithm can be upgrated, but the modernisations do not make tangible difference
-and are mainly made for some specific cases. So in our paper we are focusing on ensemble sampling, so slightly different base
-model does not change anything in resulting ensemble.
+To sample architectures we use hypernetwork. This network generates parameters for another network, which is called target network.
+Previously hypernetwoks were intended to control different characteristics such as
+complexity of architecture \citep{darts-cc} or parameters of the target model \citep{cont-learn} in several modern investigations. In our paper it controls 
+diversity of the target models, so every sampled model differs from previously sampled ones in terms of JSd.
 
-Second of all, we use hypernetwork in our sampling algorithm. Hypernetwork is small network so it does not
-consume too much computational capacity. This network contains information about another network, which is called target network.
-This approach is not new: hypernetworks and supernetworks were intended to control different characteristics such as
-complexity of acrhitecture or parameters of the target model in several modern investigations. In our algorithm it controls 
-diversity of the target models, so every sampled model differs from previously sampled ones.
-
-The hypernetwork uses Jensen-Shennon divergence (JSd) to measure difference between two architectures which is simmetric and finite
-in contrast to more popular Kullback–Leibler divergence. Our main idea of sampling different model is to use a reguralizer,
+The hypernetwork uses JSd to measure difference between two architectures which is symmetric and finite
+in contrast to more popular Kullback–Leibler divergence. Our main idea of sampling different model is to use a regularizer,
 based on JSd as a source of diversity.
@@
 This way we are able to sample deep learning models in one-shot, without and additional computational losses.
-To sum up the scheme of our method:
-\begin{enumerate} 
-    \item find a base architectire using DARTS
-    \item sample architectures in one-shot via differentiable algorithm
-    \item inferencing answer is ensemble of the sampled deep learning models
-\end{enumerate}
+To sum up the scheme of our method: find a base architecture using DARTS, sample architectures in one-shot via differentiable algorithm.
+Inference answer is ensemble of the sampled deep learning models.
 
-\printbibliography
+We conducted experiments on CIFAR and MNIST datasets to evaluate performance of the proposed method in terms of accuracy and time.
+Also we compare the performance with state-of-art NES and NAS algorithms \citep{darts, ???}.
+
+\section{Method}
+
+\subsection{Problem statement}
+
+Contrary to the selection of one single architecture in conventional NAS algorithm, this paper focuses on the problem of selecting a well-performing neural network ensemble with diverse architectures from the NAS search space, i.e., neural ensemble search (NES).
+We use following terms
+\begin{itemize}
+    \item $\alpha$ -- an architecture of a model, i.e. a set of operations between nodes
+    \item $\alpha^*$ -- a NAS resulting architecture, i.e. an optimal architecture
+    \item $w_\alpha^*$ -- optimal parameters for architecture $\alpha$
+    \item $\lambda$ -- a measure of diversity, a real number from $0$ to $\Lambda$
+    \item $\alpha(\lambda)$ -- an architecture that corresponds $\lambda$ 
+    \item $f(w_\alpha, \alpha)$ -- the output of an architecture $\alpha$ and model parameter $w_\alpha$
+    \item $S$ -- a set of architectures included into ensemble
+    \item $\mathcal{L}_{train}$, $\mathcal{L}_{val}$ -- the training and validation losses, respectively.
+We imply their dependence on preset dataset and do not denote it explicitly, because we dont deal with it
+\end{itemize}
+
+Given the ensemble scheme, NES can be formally framed as
+
+\begin{gather*}
+	\min_S \mathcal{L}_{val}\left(\frac{1}{|S|}\sum_{\alpha \in S}f(w_\alpha^*, \alpha)\right) \\
+s.t. \text{ }\forall \alpha \in S \text{ } w_\alpha^* = \arg \min_w \mathcal{L}_{train}(f(w_\alpha^*, \alpha))
+\end{gather*}
+
+We rearranged the problem:  general for all architectures. Also architectures differ in terms of $\lambda$ so resulting functions can be calculated in terms of expected values.
+
+\begin{gather*}
+    \min_{\alpha} \mathbb{E}_\lambda [\mathcal{L}_{val}(w^*, \alpha(\lambda)) - \lambda JS(\alpha^*, \alpha(\lambda))] \\
+    s.t. \text{ } w^* = \arg \min_w \mathbb{E}_\lambda[\mathcal{L}_{train}(w, \alpha(\lambda))]
+\end{gather*}
+
+\subsection{Computational experiment}
+
+In our model $\lambda$ is a random value, distributed according to uniform distribution from 0 to $\Lambda$ ($\sim U(0, \Lambda)$).
+Main goal of basic experiment was to estimate $\Lambda$ and also to investigate dependence of resulting architecture's performance on $\lambda$.
+
+\subsubsection{Experiment planning}
+
+In our basic experiment we run the algorithm on fashionMNIST dataset for several different $\lambda$ and looked at resulting architecture and accuracy.
+Further we will use $\lambda$ distributed randomly, but in basic experiment it is fixed.
+
+\subsubsection{Preliminary report}
+
+Obtained results are depicted in the table below. Maximal accuracy and amount of matching edges between resulting and optimal architecture are written down.
+
+This information allows us to choose $\Lambda = 32$.
+However amount of matching edges does not really coincide with our expectations.
+Architectures almost do not intersect.
+It can be explained by the fact that the optimized function is not convex, so algorithm fall into different minimums, however we can get more matching edges by using negative $\lambda$.
+
+\begin{table}[h   ]
+	\caption{preliminary results}
+	\centering
+	\begin{tabular}{lll}
+
+		\midrule
+		$\lambda$     & accuracy, \% & matched edges \\
+		\midrule
+        0 (optimum) & 91.24 & - \\ 
+        1/2  & 91.24 &  4   \\
+		2  & 91.26   &  3   \\
+		32 & 89.21   &  2   \\
+		64 & 87.09   &  1   \\
+		\bottomrule
+	\end{tabular}
+	\label{tab:table}
+\end{table}
+
+\bibliography{references}
 

### 2023-04-01 paper/main.tex
paper updated

@@
 \usepackage{graphicx}
+\usepackage{float}
+\usepackage{wrapfig}
 \graphicspath{{../figures}}
@@
 
-This paper introduces a new method of deep learning ensemble contsruction.
-In our research we investigate an algorithm of sampling the deep learning models using
+In our research we investigate a new method of sampling the deep learning models using
 hypernetwork.
-Hypernetwork is a neural network which controls diversity of the models.
+A hypernetwork is a neural network which controls diversity of the models.
 It translates a real number into an architecture of a sampled neural network.
@@
 
-Our method takes the result of NAS as a base architecture than it samples architectures which are close to the optimal one in terms of Jensen-Shennon divergence (JSd).
-Method can control whether sampled architectures are close enough to the optimal one so they give good results on the original dataset and are diverse enough so every architecture makes its own contribution to the final answer.
+Our method takes the result of NAS as a base architecture than it samples architectures which are close to the optimal one in terms of Jensen-Shannon divergence (JSd).
+Architectures differ in terms of $\lambda$, idea of method is shown in \hyperref[fig:arch]{Fig.
+1}.
+Basic architecture is gained with $\lambda = \lambda_1$.
+Blue ellipses are equidistant surfaces of architectures.
+Staring with diverse parameter $\lambda = \lambda_2$ resulting architecture performs unacceptable accuracy, so architectures beyond the surface are not included into ensemble.
+Method can control whether sampled architectures are close enough to the optimal one so they perform good accuracy on the original dataset and are diverse enough so every architecture makes its own contribution to the final answer.
 
-To sample architectures we use hypernetwork. This network generates parameters for another network, which is called target network.
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.6\textwidth]{fig1}
+    \caption{\label{fig:arch}Architecture space}
+\end{figure}
+
+To sample architectures we use hypernetwork \citep{hypernetworks}. This network generates parameters for another network, which is called target network.
 Previously hypernetwoks were intended to control different characteristics such as
-complexity of architecture \citep{darts-cc} or parameters of the target model \citep{cont-learn} in several modern investigations. In our paper it controls 
+complexity of architecture \citep{darts-cc} or parameters of the target model \citep{cont-learn} in several modern papers. In our paper it controls 
 diversity of the target models, so every sampled model differs from previously sampled ones in terms of JSd.
@@
 
-We conducted experiments on CIFAR and MNIST datasets to evaluate performance of the proposed method in terms of accuracy and time.
+We conduct experiments on CIFAR and MNIST datasets to evaluate performance of the proposed method in terms of accuracy and time.
 Also we compare the performance with state-of-art NES and NAS algorithms \citep{darts, ???}.
 
-\section{Method}
-
-\subsection{Problem statement}
+\section{Problem statement}
 
 Contrary to the selection of one single architecture in conventional NAS algorithm, this paper focuses on the problem of selecting a well-performing neural network ensemble with diverse architectures from the NAS search space, i.e., neural ensemble search (NES).
-We use following terms
-\begin{itemize}
-    \item $\alpha$ -- an architecture of a model, i.e. a set of operations between nodes
-    \item $\alpha^*$ -- a NAS resulting architecture, i.e. an optimal architecture
-    \item $w_\alpha^*$ -- optimal parameters for architecture $\alpha$
-    \item $\lambda$ -- a measure of diversity, a real number from $0$ to $\Lambda$
-    \item $\alpha(\lambda)$ -- an architecture that corresponds $\lambda$ 
-    \item $f(w_\alpha, \alpha)$ -- the output of an architecture $\alpha$ and model parameter $w_\alpha$
-    \item $S$ -- a set of architectures included into ensemble
-    \item $\mathcal{L}_{train}$, $\mathcal{L}_{val}$ -- the training and validation losses, respectively.
-We imply their dependence on preset dataset and do not denote it explicitly, because we dont deal with it
-\end{itemize}
+In our formal statements
+\mbox{\boldmath{$\alpha$}} denotes an architecture of a model, i.e.
+a set of operations between nodes.
+\mbox{\boldmath{$\alpha^*$}} is a NAS resulting architecture, i.e.
+an optimal architecture.
+\mbox{\boldmath{$w_\alpha^*$}} is vector of optimal parameters for architecture \mbox{\boldmath{$\alpha^*$}}.
+$\lambda$ is a measure of diversity, a real number from $0$ to $\Lambda$.
+\mbox{\boldmath{$\alpha$}}$(\lambda)$ is an architecture that corresponds $\lambda$, the architecture is gained after solving problem below.
+$f(\mbox{\boldmath{$w_\alpha$}}, \mbox{\boldmath{$\alpha$}})$ is an output of an architecture \mbox{\boldmath{$\alpha$}} and model parameter \mbox{\boldmath{$w_\alpha$}}.
+$S$ -- a set of architectures included into ensemble.
+$\mathcal{L}_{train}$, $\mathcal{L}_{val}$ are training and validation losses, respectively.
+We imply their dependence on preset dataset and do not denote it explicitly, because we do not deal with it.
 
@@
 \begin{gather*}
-	\min_S \mathcal{L}_{val}\left(\frac{1}{|S|}\sum_{\alpha \in S}f(w_\alpha^*, \alpha)\right) \\
-s.t. \text{ }\forall \alpha \in S \text{ } w_\alpha^* = \arg \min_w \mathcal{L}_{train}(f(w_\alpha^*, \alpha))
+	\min_S \mathcal{L}_{val}\left(\frac{1}{|S|}\sum_{\mbox{\boldmath{$\alpha$}} \in S}f(\mbox{\boldmath{$w_\alpha^*$}}, \mbox{\boldmath{$\alpha$}})\right) \\
+s.t.
+\text{ }\forall \mbox{\boldmath{$\alpha$}} \in S \text{ } \mbox{\boldmath{$w_\alpha^*$}} = \arg \min_{\mbox{\boldmath{$w$}}} \mathcal{L}_{train}(f(\mbox{\boldmath{$w_\alpha^*$}}, \mbox{\boldmath{$\alpha$}}))
 \end{gather*}
 
-We rearranged the problem:  general for all architectures. Also architectures differ in terms of $\lambda$ so resulting functions can be calculated in terms of expected values.
+We rearrange the problem:  general for all architectures. Also architectures differ in terms of $\lambda$ so resulting functions can be calculated in terms of expected values.
 
 \begin{gather*}
-    \min_{\alpha} \mathbb{E}_\lambda [\mathcal{L}_{val}(w^*, \alpha(\lambda)) - \lambda JS(\alpha^*, \alpha(\lambda))] \\
-    s.t. \text{ } w^* = \arg \min_w \mathbb{E}_\lambda[\mathcal{L}_{train}(w, \alpha(\lambda))]
+    \min_{\mbox{\boldmath{$\alpha$}}} \mathbb{E}_\lambda [\mathcal{L}_{val}(\mbox{\boldmath{$w^*$}}, \mbox{\boldmath{$\alpha$}}(\lambda)) - \lambda JS(\mbox{\boldmath{$\alpha^*$}}, \mbox{\boldmath{$\alpha$}}(\lambda))] \\
+    s.t. \text{ } \mbox{\boldmath{$w^*$}} = \arg \min_{\mbox{\boldmath{$w$}}} \mathbb{E}_\lambda[\mathcal{L}_{train}(\mbox{\boldmath{$w$}}, \mbox{\boldmath{$\alpha$}}(\lambda))]
 \end{gather*}
@@
 In our model $\lambda$ is a random value, distributed according to uniform distribution from 0 to $\Lambda$ ($\sim U(0, \Lambda)$).
-Main goal of basic experiment was to estimate $\Lambda$ and also to investigate dependence of resulting architecture's performance on $\lambda$.
+Main goal of basic experiment is to estimate $\Lambda$ and also to investigate dependence of resulting architecture's performance on $\lambda$.
 
@@
 
-Obtained results are depicted in the table below. Maximal accuracy and amount of matching edges between resulting and optimal architecture are written down.
+Obtained results are depicted in the table below.
+Maximal accuracy of sampled architectures is written down.
+Also we recorded amount of matched operations between nodes i.e.
+number of edges between particular nodes that contain the same operation in obtained architecture and the basic one.
 
-This information allows us to choose $\Lambda = 32$.
+This results allow us to choose $\Lambda = 32$.
 However amount of matching edges does not really coincide with our expectations.
@@
 		\midrule
-		$\lambda$     & accuracy, \% & matched edges \\
+		$\lambda$     & accuracy, \% & matched operations \\
 		\midrule
@@
 
+\section{Method}
+
+Below we briefly described our method for solving problem of classification with dataset $\mathcal{D} = (\mathbf{X}, \mathbf{y})$.
+For each object $\mathbf{x} \in \mathbf{X}$ there is a label $y \in \mathbf{y}$.
+We solve the problem via NES, sampling architectures according to novel methodology which is formally described below.
+
+\subsection{architecture}
+
+Let $\mathcal{V} = \{ 1, \ldots, N \}$ be a set of vertices, where N is a number of vertices, and $\mathcal{E} = \{ (i, j) \in V \times V \mid i < j \}$ a set of edges between them.
+$\mathcal{O}$ is a set of operations to choose from. Usually it contains pooling, convolutions, etc.
+For each edge there is an operation $o \in \mathcal{O}$ that transits information from one node to another.
+
+NAS algorithms search for optimal architecture. 
+As it was mentioned below, architecture of neural network is a set of operations between nodes.
+In NAS methods architecture is a vector constructed by following rules.
+For each edge $(i, j) \in \mathcal{E}$, \mbox{\boldmath{$\alpha^{(i, j)}$}} is a vector, which assigns impact of each operation.
+\mbox{\boldmath{$\alpha$}} is a concatenation of all structural parameters vectors \mbox{\boldmath{$\alpha^{(i, j)}$}}.
+
+\subsection{reguralizer}
+
+Source of diversity in out method is a regularizer with diversity parameter $\lambda$.
+By subtracting it from a loss function we promote method for finding an architecture which differs from the optimal one.
+
+We use Jensen-Shannon divergence to measure diversity of two architectures.
+NES algorithms give discrete architecture as a result of their work, i.e.
+initially optimal architecture \mbox{\boldmath{$\alpha_{init}^*$}} is discrete, so JSd cannot be calculated with \mbox{\boldmath{$\alpha_{init}^*$}} as an argument.
+We smooth the architecture using smooth parameter $\tau$ to solve this problem.
+$$
+\mbox{\boldmath{$\alpha^*$}} = (1 - \tau)\mbox{\boldmath{$\alpha_{init}^*$}} + \tau \frac{1}{|\mathcal{O}|}
+$$
+
+Assuming $\tau$ close to one we obtain a smoothed architecture that contains the same information about architecture as a initial one, but we also can use it in JSd.
+
+\subsection{diversity control}
+
+In order to control diversity we employ the concept of hypernetwork. A hypernetwork is a parametric mapping from $[0, \Lambda]$ to the set of model structural parameters \citep{darts-cc}.
+$$
+\mbox{\boldmath{$\alpha$}} : [0, \Lambda], \mathbb{R}^u \to \mathbb{R}^s
+$$
+Where $\mathbb{R}^u$ is a hypernetwork parametric space and $\mathbb{R}^s$ is space of model structural parameters. In this terms \mbox{\boldmath{$\alpha$}} can be redefined using hypernetwork
+
+$$
+\mbox{\boldmath{$\alpha$}} = \mbox{\boldmath{$\alpha$}}(\lambda, \mbox{\boldmath{$a$}}) \text{ or } \mbox{\boldmath{$\alpha^{(i, j)}$}} = \mbox{\boldmath{$\alpha^{(i, j)}$}}(\lambda, \mbox{\boldmath{$a^{(i, j)}$}})
+$$
+In this paper each function $\mbox{\boldmath{$\alpha^{(i, j)}$}}$ is a piecewise linear function
+$$
+\mbox{\boldmath{$\alpha^{(i, j)}$}}(\lambda, \mbox{\boldmath{$a^{(i, j)}$}}) = \sum_{k=0}^{N-1} \left( \frac{\lambda - r_k}{r_{k + 1} - r_k} \mbox{\boldmath{$a_k^{(i, j)}$}} + \left(1 - \frac{\lambda - r_k}{r_{k + 1} - r_k}\right) \mbox{\boldmath{$a_{k + 1}^{(i, j)}$}} \right) I[\lambda \in [r_k, r_{k+1}]]
+$$
+
+In our method $\lambda$ is sampled from predefined distribution $p(\lambda) = U(0, \lambda)$ and new architecture is obtained from hypernetwork.
+
 \bibliography{references}

### 2023-04-03 code/utils.py
add bayesian search w/ monte carlo

@@ -22,23 +22,47 @@ def accuracy(output, target, topk=(1,)):
 
 #==========================================================================
 
-from nni.retiarii.oneshot.pytorch import DartsTrainer
-import torch.nn.functional as F
-import torch
 import json
+
+import numpy as np
+import torch
+from nni.retiarii.oneshot.pytorch import DartsTrainer
+from nni.retiarii.oneshot.pytorch.darts import DartsLayerChoice
 
 
 def JSD(net_1_logits, net_2_logits):
     from torch.functional import F
     net_1_probs = F.softmax(net_1_logits, dim=0)
     net_2_probs = F.softmax(net_2_logits, dim=0)
-    
+
     total_m = 0.5 * (net_1_probs + net_2_probs)
-    
+
     loss = 0.0
-    loss += F.kl_div(F.log_softmax(net_1_logits, dim=0), total_m, reduction="batchmean") 
-    loss += F.kl_div(F.log_softmax(net_2_logits, dim=0), total_m, reduction="batchmean") 
+    loss += F.kl_div(F.log_softmax(net_1_logits, dim=0), total_m, reduction="batchmean")
+    loss += F.kl_div(F.log_softmax(net_2_logits, dim=0), total_m, reduction="batchmean")
     return (0.5 * loss)
+
+
+def get_optimal_probabilities(nas_modules, operations, tau):
+    O = len(operations) # кол-во операций
+
+    optimal = {} # выдает сглаженный тензор операций по названию операции
+    with open('checkpoints/0/arc.json') as f:
+        checkpoint_optimum = json.load(f) # оптимальная архитектура в виде словаря
+
+    for name, _ in nas_modules:
+        if name in checkpoint_optimum.keys() and name[-6:] != 'switch': # если ребро есть в оптимальной архитектуре и модуль не reduce_n#_switch
+            operation = checkpoint_optimum[name] # имя оптимальной операции
+
+            index = operations[operation] # индекс оптимальной операции
+            t = torch.zeros(O, device=('cuda' if torch.cuda.is_available() else 'cpu'))
+            t[index] = 1
+
+            t = t * tau + 1 / O * (1 - tau)
+
+            optimal[name] = t
+
+    return optimal
 
 
 class MyDartsTrainer(DartsTrainer):
@@ -48,32 +72,17 @@ class MyDartsTrainer(DartsTrainer):
                  device=None, log_frequency=None,
[…]

### 2023-04-03 code/search.py
add monte carlo search mode

@@ -3,7 +3,6 @@
 
 import json
 import logging
-import time
 from argparse import ArgumentParser
 
 import torch
@@ -11,8 +10,7 @@ import torch.nn as nn
 
 import datasets
 from model import CNN
-from utils import accuracy, MyDartsTrainer
-
+from utils import accuracy, MyDartsTrainer, BayesianSearchMC
 
 logger = logging.getLogger('nni')
 dataset = "fashionmnist"
@@ -28,6 +26,9 @@ if __name__ == "__main__":
     parser.add_argument("--unrolled", default=False, action="store_true")
     parser.add_argument("--visualization", default=False, action="store_true")
     parser.add_argument("--save-folder", default='checkpoints/0', type=str)
+    parser.add_argument("--tau", default=0.95, type=float, help="probability smoothing parameter")
+    parser.add_argument("--seed", default=0, type=int, help="random seed for bayesian sampling")
+    parser.add_argument("--mode", default="ours", help="random seed for bayesian sampling")
     args = parser.parse_args()
 
     dataset_train, dataset_valid = datasets.get_dataset(dataset)
@@ -42,19 +43,28 @@ if __name__ == "__main__":
     optim = torch.optim.SGD(model.parameters(), 0.025, momentum=0.9, weight_decay=3.0E-4)
     lr_scheduler = torch.optim.lr_scheduler.CosineAnnealingLR(optim, args.epochs, eta_min=0.001)
 
-    trainer = MyDartsTrainer( # MyDartsTrainer
-        model=model,
-        loss=criterion, # =mycriterion,
-        metrics=lambda output, target: accuracy(output, target, topk=(1,)),
-        optimizer=optim,
-        num_epochs=args.epochs,
-        dataset=dataset_train,
-        batch_size=args.batch_size,
-        log_frequency=args.log_frequency,
-        unrolled=args.unrolled,
-        tau=0.95, # параметр сглаживания для подсчета дивергенции
-        decay=args.decay # вес регуляризации
-    )
+    kwargs = {
+        "model": model,
+        "loss": criterion, # =mycriterion,
+        "metrics": lambda output, target: accuracy(output, target, topk=(1,)),
+        "optimizer": optim,
+        "num_epochs": args.epochs,
+        "dataset": dataset_train,
+        "batch_size": args.batch_size,
+        "log_frequency": args.log_frequency,
+        "unrolled": args.unrolled,
+        "tau": args.tau,
+    }
+
[…]

### 2023-04-03 code/utils.py
adapt to gpu + experiments

@@ -128,7 +128,7 @@ class BayesianSearchMC(DartsTrainer):
         for name, module in self.nas_modules:
             if name not in result:
                 if isinstance(module, DartsLayerChoice):
-                    idx = np.random.choice(self.O, p=np.array(self.optimal[name]))
+                    idx = np.random.choice(self.O, p=np.array(self.optimal[name].cpu()))
                     result[name] = list(module.op_choices.keys())[idx]
                 else:
                     result[name] = module.export()

### 2023-04-04 paper/main.tex
experiments + paper modified

@@
 
-\author{K. Yakovlev, O.Bakhteev, K. Petrushina, P. Babkin
+\author{P. Babkin, K. Yakovlev, K. Petrushina, O.Bakhteev,
 	%% David S.~Hippocampus\thanks{Use footnote for providing further
@@
 
-In our research we investigate a new method of sampling the deep learning models using
-hypernetwork.
-A hypernetwork is a neural network which controls diversity of the models.
-It translates a real number into an architecture of a sampled neural network.
-This method samples deep learning models in one-shot regime, without any additional calculations losses.
-To evaluate the performance of the proposed algorithm, we conduct experiments on the Fashion-MNIST and CIFAR-10
-datasets and compare the resulting ensembles with ones sampled by other searching algorithms.
+In our research, we investigate a novel method for sampling deep learning models using a hypernetwork.
+The hypernetwork is a neural network that controls the diversity of the models by translating a real number representing ensemble diversity into a sampled neural network architecture.
+Architectures are obtained in a one-shot manner by perturbing from the base architecture in terms of the Jenson-Shannon divergence (JSd).
+We evaluate the performance of the proposed algorithm by conducting experiments on the Fashion-MNIST and CIFAR-10 datasets, comparing the resulting ensembles with those sampled by other searching algorithms.
 
@@
     \includegraphics[width=0.6\textwidth]{fig1}
-    \caption{\label{fig:arch}Architecture space}
+    \caption{\label{fig:arch}Architecture space with JSd metrics.
+    Blue ellipses are equidistant surfaces.
+The space is continuous but has varying preferred operations across different architectural levels.
+Architectures with different operations are pictured separately on the picture.}
 \end{figure}
@@
 
-This way we are able to sample deep learning models in one-shot, without and additional computational losses.
+This way we sample deep learning models in one-shot unlike NES
+for Uncertainty Estimation \citep{nes}, where every sampled models must be tested and least appropriate architectures are excluded from ensemble.
+In this way our method is similar to NES via Bayesian Sampling \citep{baysiannes}, but we sample architectures using different approach, posterior distribution for architectures is gained based on the optimal one.
 To sum up the scheme of our method: find a base architecture using DARTS, sample architectures in one-shot via differentiable algorithm.
@@
 We conduct experiments on CIFAR and MNIST datasets to evaluate performance of the proposed method in terms of accuracy and time.
-Also we compare the performance with state-of-art NES and NAS algorithms \citep{darts, ???}.
+Also we compare the performance with state-of-art NES algorithms \citep{nes, baysiannes}.
 
@@
 
-Contrary to the selection of one single architecture in conventional NAS algorithm, this paper focuses on the problem of selecting a well-performing neural network ensemble with diverse architectures from the NAS search space, i.e., neural ensemble search (NES).
-In our formal statements
-\mbox{\boldmath{$\alpha$}} denotes an architecture of a model, i.e.
-a set of operations between nodes.
-\mbox{\boldmath{$\alpha^*$}} is a NAS resulting architecture, i.e.
-an optimal architecture.
-\mbox{\boldmath{$w_\alpha^*$}} is vector of optimal parameters for architecture \mbox{\boldmath{$\alpha^*$}}.
-$\lambda$ is a measure of diversity, a real number from $0$ to $\Lambda$.
-\mbox{\boldmath{$\alpha$}}$(\lambda)$ is an architecture that corresponds $\lambda$, the architecture is gained after solving problem below.
-$f(\mbox{\boldmath{$w_\alpha$}}, \mbox{\boldmath{$\alpha$}})$ is an output of an architecture \mbox{\boldmath{$\alpha$}} and model parameter \mbox{\boldmath{$w_\alpha$}}.
-$S$ -- a set of architectures included into ensemble.
-$\mathcal{L}_{train}$, $\mathcal{L}_{val}$ are training and validation losses, respectively.
-We imply their dependence on preset dataset and do not denote it explicitly, because we do not deal with it.
+In our paper, we address the problem of classification.
+We assume that the dataset $\mathcal{D} = (\mathbf{X}, \mathbf{y})$ is given, where $\mathbf{X}$ represents the feature matrix and $\mathbf{y})$ represents the target vector.
+The dataset is divided into training and validation subsets, for which the loss functions $\mathcal{L}_{train}$ and $\mathcal{L}_{val}$ are specified, respectively.
+In general, these functions depend on the feature matrix, target vector, and the predicted outputs of the training model.
+However, in our paper, we will not explicitly state their dependence on the dataset, assuming it implicitly.
+Therefore, we will state that the loss functions depend only on the predicted outputs of the model.
+
+Contrary to the selection of one single architecture in conventional NAS algorithm \citep{darts, enas, nas}, this paper focuses on the problem of selecting a well-performing neural network ensemble with diverse architectures from the NAS search space, i.e., neural ensemble search (NES).
+
+In order to facilitate our study, several key terms are defined.
+The architecture of a model, i.e.
+a set of node operations, is denoted by \mbox{\boldmath{$\alpha$}}.
+For a fixed architecture, optimal parameters are denoted by \mbox{\boldmath{$w_\alpha^*$}}.
+The optimal architecture resulting from neural architecture search (NAS) is denoted as \mbox{\boldmath{$\alpha^*$}}. 
+To quantify architectural diversity, we define $\lambda$, a real number ranging from 0 to $\Lambda$.
+The corresponding architecture for a given $\lambda$ is denoted by \mbox{\boldmath{$\alpha$}}($\lambda$), which can be obtained by solving a specific problem.
+The output of an architecture \mbox{\boldmath{$\alpha$}}, given its corresponding model parameters \mbox{\boldmath{$w_\alpha$}}, is denoted by $f$(\mbox{\boldmath{$w_\alpha$}}, \mbox{\boldmath{$\alpha$}}).
+Finally, the set of architectures included in the ensemble is denoted by $\mathcal{S}$.
 
@@
 
-We rearrange the problem:  general for all architectures. Also architectures differ in terms of $\lambda$ so resulting functions can be calculated in terms of expected values.
+\section{Method}
+
+Below we briefly described our method for solving problem of classification with dataset $\mathcal{D} = (\mathbf{X}, \mathbf{y})$.
+For each object $\mathbf{x} \in \mathbf{X}$ there is a label $y \in \mathbf{y}$.
+We solve the problem via NES, sampling architectures according to novel methodology which is formally described below.
+
+\subsection{Architecture}
+
+Let $\mathcal{V} = \{ 1, \ldots, N \}$ be a set of vertices, where N is a number of vertices, and $\mathcal{E} = \{ (i, j) \in V \times V \mid i < j \}$ a set of edges between them.
+A set of possible operations
+$\mathcal{O}$ usually contains pooling, convolutions, etc.
+For each edge there is an operation $o \in \mathcal{O}$ that transits information from one node to another.
+
+NAS algorithms search for optimal architecture. 
+As it was mentioned below, architecture of neural network is a set of operations between nodes.
+In NAS methods architecture is a vector constructed by following rules.
+For each edge $(i, j) \in \mathcal{E}$, \mbox{\boldmath{$\alpha^{(i, j)}$}} is a vector, which assigns impact of each operation.
+\mbox{\boldmath{$\alpha$}} is a concatenation of all structural parameters vectors \mbox{\boldmath{$\alpha^{(i, j)}$}}.
+
+\subsection{Reguralizer and heuristic}
+
+Source of diversity in out method is a regularizer with diversity parameter $\lambda$.
+By subtracting it from a loss function we promote method for finding an architecture which differs from the optimal one.
+
+We use Jensen-Shannon divergence to measure diversity of two architectures.
+NES algorithms give discrete architecture as a result of their work, i.e.
+initially optimal architecture \mbox{\boldmath{$\alpha_{init}^*$}} is discrete, so JSd cannot be calculated with \mbox{\boldmath{$\alpha_{init}^*$}} as an argument.
+We smooth the architecture using smooth parameter $\tau$ to solve this problem.
+$$
+\mbox{\boldmath{$\alpha^*$}} = (1 - \tau)\mbox{\boldmath{$\alpha_{init}^*$}} + \tau \frac{1}{|\mathcal{O}|}
+$$
+
+Assuming $\tau$ close to one we obtain a smoothed architecture that contains the same information about architecture as a initial one, but we also can use it in JSd.
+
+\subsection{Diversity control via hypernetwork}
+
+In order to control diversity we employ the concept of hypernetwork. A hypernetwork is a parametric mapping from $[0, \Lambda]$ to the set of model structural parameters \citep{darts-cc}.
+$$
+\mbox{\boldmath{$\alpha$}} : [0, \Lambda], \mathbb{R}^u \to \mathbb{R}^s
+$$
+Where $\mathbb{R}^u$ is a hypernetwork parametric space and $\mathbb{R}^s$ is space of model structural parameters. In this terms \mbox{\boldmath{$\alpha$}} can be redefined using hypernetwork
+
+$$
+\mbox{\boldmath{$\alpha$}} = \mbox{\boldmath{$\alpha$}}(\lambda, \mbox{\boldmath{$a$}}) \text{ or } \mbox{\boldmath{$\alpha^{(i, j)}$}} = \mbox{\boldmath{$\alpha^{(i, j)}$}}(\lambda, \mbox{\boldmath{$a^{(i, j)}$}})
+$$
+In this paper each function $\mbox{\boldmath{$\alpha^{(i, j)}$}}$ is a piecewise linear function
+$$
+\mbox{\boldmath{$\alpha^{(i, j)}$}}(\lambda, \mbox{\boldmath{$a^{(i, j)}$}}) = \sum_{k=0}^{N-1} \left( \frac{\lambda - r_k}{r_{k + 1} - r_k} \mbox{\boldmath{$a_k^{(i, j)}$}} + \left(1 - \frac{\lambda - r_k}{r_{k + 1} - r_k}\right) \mbox{\boldmath{$a_{k + 1}^{(i, j)}$}} \right) I[\lambda \in [r_k, r_{k+1}]]
+$$
+
+In our method $\lambda$ is sampled from predefined distribution $p(\lambda) = U(0, \lambda)$ and new architecture is obtained from hypernetwork.
+
+\subsection{Final statement}
+
+Upon concluding the method description, a reformulated problem can be postulated: specifically, architectures are obtained via hypernetwork, and the regularizer is subtracted from the loss function.
+A varied parameter $\lambda$, ranging from 0 to $\Lambda$, is distributed according to a uniform distribution.
 
 \begin{gather*}
-    \min_{\mbox{\boldmath{$\alpha$}}} \mathbb{E}_\lambda [\mathcal{L}_{val}(\mbox{\boldmath{$w^*$}}, \mbox{\boldmath{$\alpha$}}(\lambda)) - \lambda JS(\mbox{\boldmath{$\alpha^*$}}, \mbox{\boldmath{$\alpha$}}(\lambda))] \\
-    s.t. \text{ } \mbox{\boldmath{$w^*$}} = \arg \min_{\mbox{\boldmath{$w$}}} \mathbb{E}_\lambda[\mathcal{L}_{train}(\mbox{\boldmath{$w$}}, \mbox{\boldmath{$\alpha$}}(\lambda))]
+    \min_{\mbox{\boldmath{$\alpha$}}} \mathbb{E}_{\lambda \sim U(0, \Lambda)} [\mathcal{L}_{val}(\mbox{\boldmath{$w^*$}}, \mbox{\boldmath{$\alpha$}}(\lambda)) - \lambda JS(\mbox{\boldmath{$\alpha^*$}}, \mbox{\boldmath{$\alpha$}}(\lambda))] \\
+    s.t. \text{ } \mbox{\boldmath{$w^*$}} = \arg \min_{\mbox{\boldmath{$w$}}} \mathbb{E}_{\lambda \sim U(0, \Lambda)}[\mathcal{L}_{train}(\mbox{\boldmath{$w$}}, \mbox{\boldmath{$\alpha$}}(\lambda))]
 \end{gather*}
 
-\subsection{Computational experiment}
+Following problem resolution, a new architecture is acquired and subsequently included into the ensemble.
+It is assured that said architecture is diverse enough from its counterparts and performs an acceptable level of accuracy.
 
-In our model $\lambda$ is a random value, distributed according to uniform distribution from 0 to $\Lambda$ ($\sim U(0, \Lambda)$).
-Main goal of basic experiment is to estimate $\Lambda$ and also to investigate dependence of resulting architecture's performance on $\lambda$.
+\section{Computational experiment}
 
-\subsubsection{Experiment planning}
+Main goal of basic experiment is to investigate dependence of resulting architecture's performance on $\lambda$ and also to estimate suitable $\Lambda$.
 
-In our basic experiment we run the algorithm on fashionMNIST dataset for several different $\lambda$ and looked at resulting architecture and accuracy.
-Further we will use $\lambda$ distributed randomly, but in basic experiment it is fixed.
+We conducted experiments on fashionMNIST dataset for $\lambda = 1, \ldots, 40$ and looked at resulting architecture and accuracy.
+Then we searched for appropriate $\Lambda$ by the following algorithm: we chose three random values of $\lambda$ from 0 to $\Lambda$, ensembled corresponding architectures and looked and ensemble performance in terms of accuracy on the dataset.
 
-\subsubsection{Preliminary report}
+\subsection{Preliminary report}
 
-Obtained results are depicted in the table below.
+Obtained results of architectures investigation are depicted in the table below \hyperref[tab:prelim]{Tab.
+1}.
 Maximal accuracy of sampled architectures is written down.
@@
 number of edges between particular nodes that contain the same operation in obtained architecture and the basic one.
+Graphical visualization can be found in \hyperref[fig:graph]{Fig.
+2}.
+
+Although the graphic is unstable, deterioration of accuracy with growth of architecture diversity parameter $\lambda$ can be clearly seen.
 
@@
 	\end{tabular}
-	\label{tab:table}
+	\label{tab:prelim}
 \end{table}
 
-\section{Method}
+\section{Conclusion}
 
-Below we briefly described our method for solving problem of classification with dataset $\mathcal{D} = (\mathbf{X}, \mathbf{y})$.
-For each object $\mathbf{x} \in \mathbf{X}$ there is a label $y \in \mathbf{y}$.
-We solve the problem via NES, sampling architectures according to novel methodology which is formally described below.
-
-\subsection{architecture}
-
-Let $\mathcal{V} = \{ 1, \ldots, N \}$ be a set of vertices, where N is a number of vertices, and $\mathcal{E} = \{ (i, j) \in V \times V \mid i < j \}$ a set of edges between them.
-$\mathcal{O}$ is a set of operations to choose from. Usually it contains pooling, convolutions, etc.
-For each edge there is an operation $o \in \mathcal{O}$ that transits information from one node to another.
-
-NAS algorithms search for optimal architecture. 
-As it was mentioned below, architecture of neural network is a set of operations between nodes.
-In NAS methods architecture is a vector constructed by following rules.
-For each edge $(i, j) \in \mathcal{E}$, \mbox{\boldmath{$\alpha^{(i, j)}$}} is a vector, which assigns impact of each operation.
-\mbox{\boldmath{$\alpha$}} is a concatenation of all structural parameters vectors \mbox{\boldmath{$\alpha^{(i, j)}$}}.
-
-\subsection{reguralizer}
-
-Source of diversity in out method is a regularizer with diversity parameter $\lambda$.
-By subtracting it from a loss function we promote method for finding an architecture which differs from the optimal one.
-
-We use Jensen-Shannon divergence to measure diversity of two architectures.
-NES algorithms give discrete architecture as a result of their work, i.e.
-initially optimal architecture \mbox{\boldmath{$\alpha_{init}^*$}} is discrete, so JSd cannot be calculated with \mbox{\boldmath{$\alpha_{init}^*$}} as an argument.
-We smooth the architecture using smooth parameter $\tau$ to solve this problem.
-$$
-\mbox{\boldmath{$\alpha^*$}} = (1 - \tau)\mbox{\boldmath{$\alpha_{init}^*$}} + \tau \frac{1}{|\mathcal{O}|}
-$$
-
-Assuming $\tau$ close to one we obtain a smoothed architecture that contains the same information about architecture as a initial one, but we also can use it in JSd.
-
-\subsection{diversity control}
-
-In order to control diversity we employ the concept of hypernetwork. A hypernetwork is a parametric mapping from $[0, \Lambda]$ to the set of model structural parameters \citep{darts-cc}.
-$$
-\mbox{\boldmath{$\alpha$}} : [0, \Lambda], \mathbb{R}^u \to \mathbb{R}^s
-$$
-Where $\mathbb{R}^u$ is a hypernetwork parametric space and $\mathbb{R}^s$ is space of model structural parameters. In this terms \mbox{\boldmath{$\alpha$}} can be redefined using hypernetwork
-
-$$
-\mbox{\boldmath{$\alpha$}} = \mbox{\boldmath{$\alpha$}}(\lambda, \mbox{\boldmath{$a$}}) \text{ or } \mbox{\boldmath{$\alpha^{(i, j)}$}} = \mbox{\boldmath{$\alpha^{(i, j)}$}}(\lambda, \mbox{\boldmath{$a^{(i, j)}$}})
-$$
-In this paper each function $\mbox{\boldmath{$\alpha^{(i, j)}$}}$ is a piecewise linear function
-$$
-\mbox{\boldmath{$\alpha^{(i, j)}$}}(\lambda, \mbox{\boldmath{$a^{(i, j)}$}}) = \sum_{k=0}^{N-1} \left( \frac{\lambda - r_k}{r_{k + 1} - r_k} \mbox{\boldmath{$a_k^{(i, j)}$}} + \left(1 - \frac{\lambda - r_k}{r_{k + 1} - r_k}\right) \mbox{\boldmath{$a_{k + 1}^{(i, j)}$}} \right) I[\lambda \in [r_k, r_{k+1}]]
-$$
-
-In our method $\lambda$ is sampled from predefined distribution $p(\lambda) = U(0, \lambda)$ and new architecture is obtained from hypernetwork.
+In this paper, we proposed a novel method for sampling ensembles of deep learning models with diversity control.
+Our method utilizes a hypernetwork to generate diverse architectures by perturbing a base architecture in terms of Jensen-Shannon divergence.
+The diversity of the ensemble is controlled by a penalty term added to the loss function, which encourages the ensemble members to be diverse.
+We conducted experiments on the Fashion-MNIST dataset and demonstrated that our method performs compatible results in terms of accuracy and architectural diversity.
+Overall, our proposed method shows potential for practical applications in deep learning ensembling.
 

### 2023-04-04 code/inference.py

@@ -15,6 +15,7 @@ from model import CNN
 from nni.retiarii.oneshot.pytorch.utils import AverageMeter
 from nni.retiarii import fixed_arch
 from glob import glob
+import numpy as np
 
 logger = logging.getLogger('nni')
 
@@ -38,50 +39,59 @@ if __name__ == "__main__":
     args = parser.parse_args()
     dataset_train, dataset_valid = datasets.get_dataset("fashionmnist", cutout_length=16)
 
-    models = []
-    for dir in glob(args.checkpoints_folder + "/*"):
-        print(dir)
-        with fixed_arch(dir + "/arc.json"):
-            model = CNN(32, 1, 36, 10, args.layers, auxiliary=True)
-        model.eval()
-        model.to(device)
-        model.load_state_dict(torch.load(dir + "/mod.json"))
-        
-        models.append(model)
+    Lambdas = range(30, 42)
+    res_dict_accur = {}
+    for Lambda in Lambdas:
+        models = []
+        lambdas = np.random.choice(Lambda, size=3, replace=False) # выбранные lambda
+        print(Lambda)
+        for dir in glob(args.checkpoints_folder + "/*"):
+            if float(dir.split('\\')[-1]) in lambdas:
+            # if dir == "./checkpoints\\0":
+                print(dir)
+                with fixed_arch(dir + "/arc.json"):
+                    model = CNN(32, 1, 36, 10, args.layers, auxiliary=True)
+                model.eval()
+                model.to(device)
+                model.load_state_dict(torch.load(dir + "/mod.json"))
+                
+                models.append(model)
 
-    valid_loader = torch.utils.data.DataLoader(dataset_valid,
-                                                batch_size=args.batch_size,
-                                                shuffle=False,
-                                                num_workers=args.workers,
-                                                pin_memory=True)
-    criterion = nn.CrossEntropyLoss()
+        valid_loader = torch.utils.data.DataLoader(dataset_valid,
+                                                    batch_size=args.batch_size,
+                                                    shuffle=False,
+                                                    num_workers=args.workers,
+                                                    pin_memory=True)
+        criterion = nn.CrossEntropyLoss()
 
-    top1 = AverageMeter("top1")
-    top5 = AverageMeter("top5")
-    losses = AverageMeter("losses")
+        top1 = AverageMeter("top1")
+        top5 = AverageMeter("top5")
[…]

### 2023-04-04 code/retrain.py

@@ -118,42 +118,49 @@ if __name__ == "__main__":
 
     args = parser.parse_args()
     dataset_train, dataset_valid = datasets.get_dataset("fashionmnist", cutout_length=16)
+    
+    best_top1s = []
+    for decay in [29, 30, 31, 32, 33, 34, 35, 36, 37, 38, 39, 40]:
+        print(f"checkpoints/{decay}")
+        with fixed_arch(f"checkpoints/{decay}" + "/arc.json"):
+        # with fixed_arch(args.save_folder + "/arc.json"):
+            model = CNN(32, 1, 36, 10, args.layers, auxiliary=True)
+        criterion = nn.CrossEntropyLoss()
 
-    with fixed_arch(args.save_folder + "/arc.json"):
-        model = CNN(32, 1, 36, 10, args.layers, auxiliary=True)
-    criterion = nn.CrossEntropyLoss()
+        model.to(device)
+        criterion.to(device)
 
-    model.to(device)
-    criterion.to(device)
+        optimizer = torch.optim.SGD(model.parameters(), 0.025, momentum=0.9, weight_decay=3.0E-4)
+        lr_scheduler = torch.optim.lr_scheduler.CosineAnnealingLR(optimizer, args.epochs, eta_min=1E-6)
 
-    optimizer = torch.optim.SGD(model.parameters(), 0.025, momentum=0.9, weight_decay=3.0E-4)
-    lr_scheduler = torch.optim.lr_scheduler.CosineAnnealingLR(optimizer, args.epochs, eta_min=1E-6)
+        train_loader = torch.utils.data.DataLoader(dataset_train,
+                                                batch_size=args.batch_size,
+                                                shuffle=True,
+                                                num_workers=args.workers,
+                                                pin_memory=True)
+        valid_loader = torch.utils.data.DataLoader(dataset_valid,
+                                                batch_size=args.batch_size,
+                                                shuffle=False,
+                                                num_workers=args.workers,
+                                                pin_memory=True)
 
-    train_loader = torch.utils.data.DataLoader(dataset_train,
-                                               batch_size=args.batch_size,
-                                               shuffle=True,
-                                               num_workers=args.workers,
-                                               pin_memory=True)
-    valid_loader = torch.utils.data.DataLoader(dataset_valid,
-                                               batch_size=args.batch_size,
-                                               shuffle=False,
[…]

### 2023-04-04 code/search.py

@@ -22,7 +22,7 @@ if __name__ == "__main__":
     parser.add_argument("--layers", default=1, type=int)
     parser.add_argument("--batch-size", default=64, type=int)
     parser.add_argument("--log-frequency", default=10, type=int)
-    parser.add_argument("--epochs", default=10, type=int)
+    parser.add_argument("--epochs", default=50, type=int)
     parser.add_argument("--channels", default=16, type=int)
     parser.add_argument("--decay", default=0.0, type=float, help='regularization coefficient')
     parser.add_argument("--unrolled", default=False, action="store_true")
@@ -32,30 +32,32 @@ if __name__ == "__main__":
 
     dataset_train, dataset_valid = datasets.get_dataset(dataset)
 
-    if dataset == "fashionmnist":
-        model = CNN(32, 1, args.channels, 10, args.layers)
-    if dataset == "cifar10":
-        model = CNN(32, 3, args.channels, 10, args.layers)
 
-    criterion = nn.CrossEntropyLoss() # mycriterion()
+    for decay in [29, 30, 31, 32, 33, 34, 35, 36, 37, 38, 39, 40]:
+        print(f"decay = {decay}")
+        if dataset == "fashionmnist":
+            model = CNN(32, 1, args.channels, 10, args.layers)
+        if dataset == "cifar10":
+            model = CNN(32, 3, args.channels, 10, args.layers)
 
-    optim = torch.optim.SGD(model.parameters(), 0.025, momentum=0.9, weight_decay=3.0E-4)
-    lr_scheduler = torch.optim.lr_scheduler.CosineAnnealingLR(optim, args.epochs, eta_min=0.001)
-
-    trainer = MyDartsTrainer( # MyDartsTrainer
-        model=model,
-        loss=criterion, # =mycriterion,
-        metrics=lambda output, target: accuracy(output, target, topk=(1,)),
-        optimizer=optim,
-        num_epochs=args.epochs,
-        dataset=dataset_train,
-        batch_size=args.batch_size,
-        log_frequency=args.log_frequency,
-        unrolled=args.unrolled,
-        tau=0.95, # параметр сглаживания для подсчета дивергенции
-        decay=args.decay # вес регуляризации
-    )
-    trainer.fit()
-    final_architecture = trainer.export()
-    print('Final architecture:', trainer.export())
-    json.dump(trainer.export(), open(args.save_folder + '/arc.json', 'w+'))
+        criterion = nn.CrossEntropyLoss() # mycriterion()
[…]

### 2023-04-04 paper/main.tex
paper updated: updated computational experiment

@@
 \usepackage{amsmath}
-
+\usepackage{caption}
+\usepackage{subcaption}
 \usepackage{doi}
@@
 
-Main goal of basic experiment is to investigate dependence of resulting architecture's performance on $\lambda$ and also to estimate suitable $\Lambda$.
+First goal of computational experiment is to investigate dependence of resulting architecture's performance on $\lambda$ and also to estimate suitable $\Lambda$.
+We conducted experiments on fashionMNIST dataset for $\lambda = 1, \ldots, 40$ and looked at resulting architecture and accuracy.
+Second goal is to investigate effectiveness of ensembling.
+We investigated how to choose architectures that on one hand are diverse enough and on other hand perform accaptable accuracy.
 
-We conducted experiments on fashionMNIST dataset for $\lambda = 1, \ldots, 40$ and looked at resulting architecture and accuracy.
-Then we searched for appropriate $\Lambda$ by the following algorithm: we chose three random values of $\lambda$ from 0 to $\Lambda$, ensembled corresponding architectures and looked and ensemble performance in terms of accuracy on the dataset.
+\subsection{Comparison of architectures}
 
-\subsection{Preliminary report}
+The results of the investigation into various neural network architectures are presented in \hyperref[tab:prelim]{Tab. 1}.
+The table displays the maximum accuracy achieved by the sampled architectures, along with the number of matched operations between nodes.
+Last one indicates the number of edges between nodes that contain the same operation in the obtained architecture and the basic architecture, gained from NAS.
+The graphical visualization of the architectures can be found in \hyperref[fig:graph1]{Fig. 2}.
 
-Obtained results of architectures investigation are depicted in the table below \hyperref[tab:prelim]{Tab.
-1}.
-Maximal accuracy of sampled architectures is written down.
-Also we recorded amount of matched operations between nodes i.e.
-number of edges between particular nodes that contain the same operation in obtained architecture and the basic one.
-Graphical visualization can be found in \hyperref[fig:graph]{Fig.
-2}.
+\begin{figure}[h]
+	\centering
+	\begin{subfigure}{.5\textwidth}
+	  \centering
+	  \includegraphics[width=1\linewidth]{fig2}
+	  \caption{Dependence of accuracy on diverse parameter $\lambda$}
+	  \label{fig:graph1}
+	\end{subfigure}%
+	\begin{subfigure}{.5\textwidth}
+	  \centering
+	  \includegraphics[width=1\linewidth]{fig3}
+	  \caption{Dependence of matching edges number on diverse parameter $\lambda$}
+	  \label{fig:graph2}
+	\end{subfigure}
+	\caption{Graphical results of computational experiment}
+	\label{fig:graph}
+\end{figure}
 
-Although the graphic is unstable, deterioration of accuracy with growth of architecture diversity parameter $\lambda$ can be clearly seen.
-
-This results allow us to choose $\Lambda = 32$.
-However amount of matching edges does not really coincide with our expectations.
-Architectures almost do not intersect.
-It can be explained by the fact that the optimized function is not convex, so algorithm fall into different minimums, however we can get more matching edges by using negative $\lambda$.
+Although the instability of the graph presented in \hyperref[fig:graph1]{Fig.2(a)} is noticeable, it is evident that the accuracy decreases as the architecture diversity parameter $\lambda$ increases.
+However, contrary to our expectations, the amount of intersecting edges depicted in \hyperref[fig:graph2]{Fig.2(b)} does not align with our anticipated results.
+The reason for this can be attributed to the non-convexity of the optimized function, which causes the algorithm to converge to different minima.
+However, we can obtain a higher number of intersecting edges by using a negative $\lambda$.
 
@@
 	\begin{tabular}{lll}
-
 		\midrule
@@
 
+\subsection{Ensembling effectiveness investigation}
+
+To investigate the effectiveness of ensembling, we employed the following methodology.
+We randomly sampled several architectures corresponding to different diverse parameters $\lambda$ chosen randomly and uniformaly from a range of 0 to $\Lambda$.
+The obtained architectures were then included in an ensemble, and the accuracy of the resulting ensemble was measured.
+By changing the diversity limit $\Lambda$, we were able to control the diversity of our deep learning models.
+The graphical results of our experiment are depicted in \hyperref[fig:graph3]{Fig.3}.
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.6\textwidth]{fig4}
+    \caption{\label{fig:graph3} Dependance of effectiveness of deep learning models ensemble on diversity limit $\Lambda$}
+\end{figure}
+
 \section{Conclusion}
@@
 We conducted experiments on the Fashion-MNIST dataset and demonstrated that our method performs compatible results in terms of accuracy and architectural diversity.
-Overall, our proposed method shows potential for practical applications in deep learning ensembling.
+Overall, our proposed method shows potential for practical applications in deep learning ensembling. asddasd
 

### 2023-04-12 paper/main.tex
paper updated

@@
 \usepackage{subcaption}
+\usepackage{doi}
+\usepackage{algorithm}
+\usepackage{algpseudocode}
+\usepackage{amssymb}
+
 \usepackage{doi}
@@
 
+Let $\mathcal{V} = \{ 1, \ldots, N \}$ be a set of vertices, where N is a number of vertices, and $\mathcal{E} = \{ (i, j) \in V \times V \mid i < j \}$ a set of edges between them.
+A set of possible operations
+$\mathcal{O}$ usually contains pooling, convolutions, etc.
+For each edge there is an operation $o \in \mathcal{O}$ that transits information from one node to another.
+
 Contrary to the selection of one single architecture in conventional NAS algorithm \citep{darts, enas, nas}, this paper focuses on the problem of selecting a well-performing neural network ensemble with diverse architectures from the NAS search space, i.e., neural ensemble search (NES).
@@
 
-Let $\mathcal{V} = \{ 1, \ldots, N \}$ be a set of vertices, where N is a number of vertices, and $\mathcal{E} = \{ (i, j) \in V \times V \mid i < j \}$ a set of edges between them.
-A set of possible operations
-$\mathcal{O}$ usually contains pooling, convolutions, etc.
-For each edge there is an operation $o \in \mathcal{O}$ that transits information from one node to another.
-
 NAS algorithms search for optimal architecture. 
@@
 $$
-\mbox{\boldmath{$\alpha$}} : [0, \Lambda], \mathbb{R}^u \to \mathbb{R}^s
+\mbox{\boldmath{$\alpha$}} : [0, \Lambda] \times \mathbb{R}^u \to \mathbb{R}^s
 $$
@@
 \begin{gather*}
-    \min_{\mbox{\boldmath{$\alpha$}}} \mathbb{E}_{\lambda \sim U(0, \Lambda)} [\mathcal{L}_{val}(\mbox{\boldmath{$w^*$}}, \mbox{\boldmath{$\alpha$}}(\lambda)) - \lambda JS(\mbox{\boldmath{$\alpha^*$}}, \mbox{\boldmath{$\alpha$}}(\lambda))] \\
+        \min_{\mbox{\boldmath{$\alpha$}}} \mathbb{E}_{\lambda \sim U(0, \Lambda)} [\mathcal{L}_{val}(w^*, \mbox{\boldmath{$\alpha$}}(\lambda)) - \lambda JS(\mbox{\boldmath{$\alpha^*$}}, \mbox{\boldmath{$\alpha$}}(\lambda))] \\
     s.t. \text{ } \mbox{\boldmath{$w^*$}} = \arg \min_{\mbox{\boldmath{$w$}}} \mathbb{E}_{\lambda \sim U(0, \Lambda)}[\mathcal{L}_{train}(\mbox{\boldmath{$w$}}, \mbox{\boldmath{$\alpha$}}(\lambda))]
@@
 It is assured that said architecture is diverse enough from its counterparts and performs an acceptable level of accuracy.
+Formal algorithm is written down as \hyperref[alg:1]{Algorithm 1}.
+\begin{figure}[h]  
+  \begin{minipage}{.6\linewidth}
+    \begin{algorithm}[H]
+    \caption{}\label{alg:1}
+        \begin{algorithmic}
+                \State Initialize: $N \in \mathbb{N}$, $\mathcal{S} = \varnothing$, hypernetwork
+            \State $S \gets \{ \mbox{\boldmath{$\alpha^*$}} \}$ \Comment{Result os NAS}
+            \For{$i = 1, \ldots, N$}
+                \State Sample $\lambda \sim U(0, \Lambda)$
+                \State $\mathcal{S} \gets \mathcal{S} \cup \{ \alpha(\lambda, \mbox{\boldmath{$\alpha^*$}}) \}$ \Comment{$\alpha$ gaind from hypernetwork}
+            \EndFor
+            \State \textbf{Return:} S as a resulting ensemble
+        \end{algorithmic}
+    \end{algorithm}
+  \end{minipage}
+\end{figure}
 
@@
 
-First goal of computational experiment is to investigate dependence of resulting architecture's performance on $\lambda$ and also to estimate suitable $\Lambda$.
-We conducted experiments on fashionMNIST dataset for $\lambda = 1, \ldots, 40$ and looked at resulting architecture and accuracy.
+In this study, we conducted a series of experiments on the fashionMNIST dataset \citep{xiao2017fashion} using a convolutional neural network (CNN) model.
+Specifically, we utilized a one-layer architecture with six nodes and seven possible operations for each edge, as outlined in the DARTS methodology \cite{darts}.
+Our optimizer was stochastic gradient descent (SGD), and we employed a cosine annealing learning rate scheduler with a minimum learning rate of 0.001.
+The loss criterion utilized in this study was CrossEntropyLoss.
+
+First goal of computational experiment is to investigate dependence of resulting architecture's performance and their diversity on $\lambda$.
 Second goal is to investigate effectiveness of ensembling.
-We investigated how to choose architectures that on one hand are diverse enough and on other hand perform accaptable accuracy.
+Main question is how to choose architectures that on one hand are diverse enough and on other hand perform acceptable accuracy.
 
 \subsection{Comparison of architectures}
+
+We employed the Differentiable Architecture Search (DARTS) algorithm to sample a base architecture with $\lambda = 0$.
+Subsequently, we sampled architectures for values of $\lambda$ ranging from 1 to 40, recording the resulting architectural structures and their corresponding classification performance.
+Specifically, we sought to examine the impact of varying levels of architectural diversity on model accuracy, with the aim of identifying optimal architectures for the given task.
 
@@
 
+\begin{table}[h   ]
+	\centering
+	\begin{tabular}{lll}
+		\midrule
+		$\lambda$     & accuracy, \% & matched operations \\
+		\midrule
+        0 (optimum) & 92.10 & 18 \\ 
+        5  & 89.66 &  2   \\
+		10  & 90.59   &  2   \\
+		15 & 90.09   &  1   \\
+		20 & 88.52   &  1   \\
+      25 & 88.54   &  1   \\
+      30 & 87.42   &  2   \\
+      35 & 86.41   &  1   \\
+      40 & 88.67   &  2  \\
+      \hline
+    \vspace{0.1cm}      
+	\end{tabular}
+    \caption{Table to test captions and labels.}
+	\label{tab:prelim}
+\end{table}
+
 \begin{figure}[h]
 	\centering
-	\begin{subfigure}{.5\textwidth}
+	\begin{subfigure}{.46\textwidth}
         \centering
 	    \includegraphics[width=1\linewidth]{fig2}
-	  \caption{Dependence of accuracy on diverse parameter $\lambda$}
+	  \caption{Dependence of performed accuracy on diversity parameter $\lambda$}
 	  \label{fig:graph1}
 	\end{subfigure}%
-	\begin{subfigure}{.5\textwidth}
+    \hspace{1cm}
+	\begin{subfigure}{.46\textwidth}
 	  \centering
 	  \includegraphics[width=1\linewidth]{fig3}
-	  \caption{Dependence of matching edges number on diverse parameter $\lambda$}
+	  \caption{Dependence of matching edges number on diversity parameter $\lambda$}
 	  \label{fig:graph2}
@@
 
-\begin{table}[h   ]
-	\caption{preliminary results}
-	\centering
-	\begin{tabular}{lll}
-		\midrule
-		$\lambda$     & accuracy, \% & matched operations \\
-		\midrule
-        0 (optimum) & 91.24 & - \\ 
-        1/2  & 91.24 &  4   \\
-		2  & 91.26   &  3   \\
-		32 & 89.21   &  2   \\
-		64 & 87.09   &  1   \\
-		\bottomrule
-	\end{tabular}
-	\label{tab:prelim}
-\end{table}
-
 \subsection{Ensembling effectiveness investigation}
@@
 To investigate the effectiveness of ensembling, we employed the following methodology.
-We randomly sampled several architectures corresponding to different diverse parameters $\lambda$ chosen randomly and uniformaly from a range of 0 to $\Lambda$.
+We randomly sampled three architectures corresponding to different diverse parameters $\lambda$ chosen randomly and uniformly from a range of 0 to $\Lambda$.
 The obtained architectures were then included in an ensemble, and the accuracy of the resulting ensemble was measured.
@@
 
-\begin{figure}[h]
+\begin{figure}[H]
     \centering
-    \includegraphics[width=0.6\textwidth]{fig4}
-    \caption{\label{fig:graph3} Dependance of effectiveness of deep learning models ensemble on diversity limit $\Lambda$}
+    \includegraphics[width=0.55\textwidth]{fig4}
+    \caption{\label{fig:graph3} Dependence of effectiveness of deep learning models ensemble on diversity limit $\Lambda$}
 \end{figure}
@@
 We conducted experiments on the Fashion-MNIST dataset and demonstrated that our method performs compatible results in terms of accuracy and architectural diversity.
-Overall, our proposed method shows potential for practical applications in deep learning ensembling. asddasd
+Overall, our proposed method shows potential for practical applications in deep learning ensembling.
 

### 2023-10-21 code/search.py
edge edg

@@ -22,18 +22,19 @@ if __name__ == "__main__":
     parser.add_argument("--layers", default=1, type=int)
     parser.add_argument("--batch-size", default=64, type=int)
     parser.add_argument("--log-frequency", default=10, type=int)
-    parser.add_argument("--epochs", default=50, type=int)
+    parser.add_argument("--epochs", default=1, type=int)
     parser.add_argument("--channels", default=16, type=int)
-    parser.add_argument("--decay", default=0.0, type=float, help='regularization coefficient')
     parser.add_argument("--unrolled", default=False, action="store_true")
     parser.add_argument("--visualization", default=False, action="store_true")
     parser.add_argument("--save-folder", default='checkpoints/0', type=str)
+    parser.add_argument("--weight", default=0.0, type=float, help='weight')
+    parser.add_argument("--lambd", default=0.0, type=float, help='lambda')
     args = parser.parse_args()
 
     dataset_train, dataset_valid = datasets.get_dataset(dataset)
 
 
-    for decay in [29, 30, 31, 32, 33, 34, 35, 36, 37, 38, 39, 40]:
+    for decay in [29]:
         print(f"decay = {decay}")
         if dataset == "fashionmnist":
             model = CNN(32, 1, args.channels, 10, args.layers)
@@ -53,11 +54,11 @@ if __name__ == "__main__":
             batch_size=args.batch_size,
             log_frequency=args.log_frequency,
             unrolled=args.unrolled,
-            tau=0.95, # параметр сглаживания для подсчета дивергенции
-            decay=decay # вес регуляризации
+            weight=args.weight, # параметр сглаживания для подсчета дивергенции
+            lambd=args.lambd # вес регуляризации
         )
         trainer.fit()
         final_architecture = trainer.export()
         print('Final architecture:', trainer.export())
-        json.dump(trainer.export(), open(f"checkpoints/{decay}" + '/arc.json', 'w+'))
+        json.dump(trainer.export(), open(f"checkpoints/lambd={args.lambd}" + '/arc.json', 'w+'))
     

### 2023-10-21 code/utils.py

@@ -1,6 +1,3 @@
-# Copyright (c) Microsoft Corporation.
-# Licensed under the MIT license.
-
 def accuracy(output, target, topk=(1,)):
     """ Computes the precision@k for the specified values of k """
     maxk = max(topk)
@@ -26,6 +23,7 @@ from nni.retiarii.oneshot.pytorch import DartsTrainer
 import torch.nn.functional as F
 import torch
 import json
+from torch.distributions import RelaxedOneHotCategorical
 
 
 def JSD(net_1_logits, net_2_logits):
@@ -46,36 +44,57 @@ class MyDartsTrainer(DartsTrainer):
                  num_epochs, dataset, grad_clip=5.,
                  learning_rate=2.5E-3, batch_size=64, workers=4,
                  device=None, log_frequency=None,
-                 arc_learning_rate=3.0E-4, unrolled=False, tau=0.95, decay=0):
+                 arc_learning_rate=3.0E-4, unrolled=False,
+                 weight=1e3, 
+                 lambd=0, 
+                 tau=0.9, 
+                 t_alpha=0.3, t_beta=0.4,
+                 optimalPath='checkpoints/fashionMNIST/optimal/arc.json', 
+                 train_as_optimal=False):
         super().__init__(model, loss, metrics, optimizer,
                  num_epochs, dataset, grad_clip,
                  learning_rate, batch_size, workers,
                  device, log_frequency,
                  arc_learning_rate, unrolled)
+        self.weight = weight
+        self.lambd = lambd
         self.tau = tau
-        self.decay = decay
+        self.t_alpha = t_alpha
+        self.t_beta = t_beta
+        self.train_as_optimal = train_as_optimal
+
+        if train_as_optimal:
+            return
         
         operations = { "maxpool": 0, "avgpool": 1, "skipconnect": 2, "sepconv3x3": 3,
                       "sepconv5x5": 4, "dilconv3x3" : 5, "dilconv5x5" : 6 } # индексы операций по названиям (в соответствии с nas_modules)
         O = len(operations) # кол-во операций
 
-        self.optimal = {} # выдает сглаженный тензор операций по названию операции
-        with open('checkpoints/0/arc.json') as f:
-            checkpoint_optimum = json.load(f) # оптимальная архитектура в виде словаря
+        self.optimal_arc = {} # выдает сглаженный тензор операций по названию операции
+        with open(optimalPath) as f:
+            self.checkpoint_optimum = json.load(f) # оптимальная архитектура в виде словаря
 
[…]

### 2023-10-21 paper/main.tex

@@
 \usepackage[utf8]{inputenc}
-\usepackage[english, russian]{babel}
+\usepackage[english]{babel}
 \usepackage[T1]{fontenc}
@@
 results in different applied problems \citep{multi-head}.
-Our paper investigates an method of sampling deep learning models in a new way that gives compatible results and has its own sphere
+Our paper investigates the method of sampling deep learning models in a new way that gives compatible results and has its own sphere
 of implementations.
@@
 Our method takes the result of NAS as a base architecture than it samples architectures which are close to the optimal one in terms of Jensen-Shannon divergence (JSd).
-Architectures differ in terms of $\lambda$, idea of method is shown in \hyperref[fig:arch]{Fig.
-1}.
-Basic architecture is gained with $\lambda = \lambda_1$.
+JSd is used to measure distance between two distributions and is symmetric and finite in contrast to more popular Kullback–Leibler divergence.
+In our investigation we consider preferences of operations between nodes of architecture to be a discrete distribution so we can measure distance between them in terms of JSd.
+
+Architectures differ in terms of $\lambda$, idea of method is shown in \hyperref[fig:arch]{Fig. 1}. Basic architecture is gained with $\lambda = \lambda_1$.
 Blue ellipses are equidistant surfaces of architectures.
@@
 
-The hypernetwork uses JSd to measure difference between two architectures which is symmetric and finite
-in contrast to more popular Kullback–Leibler divergence. Our main idea of sampling different model is to use a regularizer,
+The hypernetwork uses JSd to measure difference between two architectures. Our main idea of sampling different model is to use a regularizer,
 based on JSd as a source of diversity.
@@
 In our paper, we address the problem of classification.
-We assume that the dataset $\mathcal{D} = (\mathbf{X}, \mathbf{y})$ is given, where $\mathbf{X}$ represents the feature matrix and $\mathbf{y})$ represents the target vector.
+We assume that the dataset $\mathcal{D} = (\mathbf{X}, \mathbf{y})$ is given, where $\mathbf{X}$ represents the feature matrix and $\mathbf{y}$ represents the target vector.
 The dataset is divided into training and validation subsets, for which the loss functions $\mathcal{L}_{train}$ and $\mathcal{L}_{val}$ are specified, respectively.
@@
 
-Contrary to the selection of one single architecture in conventional NAS algorithm \citep{darts, enas, nas}, this paper focuses on the problem of selecting a well-performing neural network ensemble with diverse architectures from the NAS search space, i.e., neural ensemble search (NES).
+Contrary to the selection of one single architecture in conventional NAS algorithm \citep{darts, enas, nas}, this paper focuses on the problem of selecting a well-performing neural network ensemble with diverse architectures from the NAS search space, i.e.
+neural ensemble search (NES).
 
@@
 For a fixed architecture, optimal parameters are denoted by \mbox{\boldmath{$w_\alpha^*$}}.
-The optimal architecture resulting from neural architecture search (NAS) is denoted as \mbox{\boldmath{$\alpha^*$}}. 
+The optimal architecture resulting from neural architecture search is denoted as \mbox{\boldmath{$\alpha^*$}}. 
 To quantify architectural diversity, we define $\lambda$, a real number ranging from 0 to $\Lambda$.
 The corresponding architecture for a given $\lambda$ is denoted by \mbox{\boldmath{$\alpha$}}($\lambda$), which can be obtained by solving a specific problem.
-The output of an architecture \mbox{\boldmath{$\alpha$}}, given its corresponding model parameters \mbox{\boldmath{$w_\alpha$}}, is denoted by $f$(\mbox{\boldmath{$w_\alpha$}}, \mbox{\boldmath{$\alpha$}}).
+The output of an architecture \mbox{\boldmath{$\alpha$}}, given its corresponding model parameters \mbox{\boldmath{$w_\alpha$}}, is denoted by $f$(\mbox{\boldmath{$w_\alpha$}},~\mbox{\boldmath{$\alpha$}}).
 Finally, the set of architectures included in the ensemble is denoted by $\mathcal{S}$.
@@
 s.t.
-\text{ }\forall \mbox{\boldmath{$\alpha$}} \in S \text{ } \mbox{\boldmath{$w_\alpha^*$}} = \arg \min_{\mbox{\boldmath{$w$}}} \mathcal{L}_{train}(f(\mbox{\boldmath{$w_\alpha^*$}}, \mbox{\boldmath{$\alpha$}}))
+\text{ }\forall \mbox{\boldmath{$\alpha$}} \in S \text{ } \mbox{\boldmath{$w_\alpha^*$}} = \arg \min_{\mbox{\boldmath{$w$}}} \mathcal{L}_{train}(f(\mbox{\boldmath{$w_\alpha$}}, \mbox{\boldmath{$\alpha$}}))
 \end{gather*}
@@
 
-Below we briefly described our method for solving problem of classification with dataset $\mathcal{D} = (\mathbf{X}, \mathbf{y})$.
+Above we briefly described our method for solving problem of classification with dataset $\mathcal{D} = (\mathbf{X}, \mathbf{y})$.
 For each object $\mathbf{x} \in \mathbf{X}$ there is a label $y \in \mathbf{y}$.
@@
 
-\subsection{Reguralizer and heuristic}
+\subsection{Regularizer and heuristic}
 
@@
 Where $\mathbb{R}^u$ is a hypernetwork parametric space and $\mathbb{R}^s$ is space of model structural parameters. In this terms \mbox{\boldmath{$\alpha$}} can be redefined using hypernetwork
-
 $$
@@
 Formal algorithm is written down as \hyperref[alg:1]{Algorithm 1}.
+Ensembles of deep learning models typically consist of a small number of models, thus we recomend to take the number of models $N$ in the resulting ensemble $S$ in range from 3 to 8.
 \begin{figure}[h]  
@@
         \centering
-	    \includegraphics[width=1\linewidth]{fig2}
+	    \includegraphics[width=1\linewidth]{fig2fashion}
 	  \caption{Dependence of performed accuracy on diversity parameter $\lambda$}
-	  \label{fig:graph1}
+	  \label{fig:graph1fashion}
 	\end{subfigure}%
@@
 	  \centering
-	  \includegraphics[width=1\linewidth]{fig3}
+	  \includegraphics[width=1\linewidth]{fig3fashion}
 	  \caption{Dependence of matching edges number on diversity parameter $\lambda$}
-	  \label{fig:graph2}
+	  \label{fig:graph2fashion}
 	\end{subfigure}
-	\caption{Graphical results of computational experiment}
-	\label{fig:graph}
+	\caption{Graphical results of computational experiment on dataset fashionMNIST}
+	\label{fig:graphfashion}
 \end{figure}
 
-Although the instability of the graph presented in \hyperref[fig:graph1]{Fig.2(a)} is noticeable, it is evident that the accuracy decreases as the architecture diversity parameter $\lambda$ increases.
-However, contrary to our expectations, the amount of intersecting edges depicted in \hyperref[fig:graph2]{Fig.2(b)} does not align with our anticipated results.
+\begin{figure}[H]
+	\centering
+	\begin{subfigure}{.46\textwidth}
+        \centering
+	    \includegraphics[width=1\linewidth]{fig2CIFAR}
+	  \caption{Dependence of performed accuracy on diversity parameter $\lambda$}
+	  \label{fig:graph1CIFAR}
+	\end{subfigure}%
+    \hspace{1cm}
+	\begin{subfigure}{.46\textwidth}
+	  \centering
+	  \includegraphics[width=1\linewidth]{fig3CIFAR}
+	  \caption{Dependence of matching edges number on diversity parameter $\lambda$}
+	  \label{fig:graph2CIFAR}
+	\end{subfigure}
+	\caption{Graphical results of computational experiment on dataset CIFAR10}
+	\label{fig:graphCIFAR}
+\end{figure}
+
+Although the instability of the graph presented in \hyperref[fig:graph1fashion]{Fig.2(a)} and \hyperref[fig:graph1CIFAR]{Fig.3(a)} is noticeable, it is evident that the accuracy decreases as the architecture diversity parameter $\lambda$ increases.
+However, contrary to our expectations, the amount of intersecting edges depicted in \hyperref[fig:graph2fashion]{Fig.2(b)} and \hyperref[fig:graph2CIFAR]{Fig.3(b)} does not align with our anticipated results.
 The reason for this can be attributed to the non-convexity of the optimized function, which causes the algorithm to converge to different minima.
@@
 By changing the diversity limit $\Lambda$, we were able to control the diversity of our deep learning models.
-The graphical results of our experiment are depicted in \hyperref[fig:graph3]{Fig.3}.
+The graphical results of our experiment are depicted in \hyperref[fig:graph4]{Fig.4}.
 
-\begin{figure}[H]
+\begin{figure}[h]
 	\centering
-    \includegraphics[width=0.55\textwidth]{fig4}
+	\begin{subfigure}{.46\textwidth}
+        \centering
+	    \includegraphics[width=1\linewidth]{fig4fashion}
+	  \caption{Experiments on fashionMNIST.}
+	  \label{fig:graph4fashion}
+	\end{subfigure}%
+    \hspace{1cm}
+	\begin{subfigure}{.46\textwidth}
+	  \centering
+	  \includegraphics[width=1\linewidth]{fig4CIFAR}
+	  \caption{Experiments on CIFAR10.}
+	  \label{fig:graph4CIFAR}
+	\end{subfigure}
 	\caption{\label{fig:graph3} Dependence of effectiveness of deep learning models ensemble on diversity limit $\Lambda$}
+	\label{fig:graph4}
 \end{figure}

### 2023-10-23 code/retrain.py
new edge regularizer

@@ -41,11 +41,11 @@ def train(config, train_loader, model, optimizer, criterion, epoch):
         optimizer.zero_grad()
         logits, aux_logits = model(x)
         loss = criterion(logits, y)
-        if config.aux_weight > 0.:
-            loss += config.aux_weight * criterion(aux_logits, y)
+        if config['aux_weight'] > 0.:
+            loss += config['aux_weight'] * criterion(aux_logits, y)
         loss.backward()
         # gradient clipping
-        nn.utils.clip_grad_norm_(model.parameters(), config.grad_clip)
+        nn.utils.clip_grad_norm_(model.parameters(), config['grad_clip'])
         optimizer.step()
 
         accuracy = utils.accuracy(logits, y, topk=(1, 5))
@@ -56,16 +56,16 @@ def train(config, train_loader, model, optimizer, criterion, epoch):
         writer.add_scalar("acc1/train", accuracy["acc1"], global_step=cur_step)
         writer.add_scalar("acc5/train", accuracy["acc5"], global_step=cur_step)
 
-        if step % config.log_frequency == 0 or step == len(train_loader) - 1:
+        if step % config['log_frequency'] == 0 or step == len(train_loader) - 1:
             logger.info(
                 "Train: [{:3d}/{}] Step {:03d}/{:03d} Loss {losses.avg:.3f} "
                 "Prec@(1,5) ({top1.avg:.1%}, {top5.avg:.1%})".format(
-                    epoch + 1, config.epochs, step, len(train_loader) - 1, losses=losses,
+                    epoch + 1, config['epochs'], step, len(train_loader) - 1, losses=losses,
                     top1=top1, top5=top5))
 
         cur_step += 1
 
-    logger.info("Train: [{:3d}/{}] Final Prec@1 {:.4%}".format(epoch + 1, config.epochs, top1.avg))
+    logger.info("Train: [{:3d}/{}] Final Prec@1 {:.4%}".format(epoch + 1, config['epochs'], top1.avg))
 
 
 def validate(config, valid_loader, model, criterion, epoch, cur_step):
@@ -88,79 +88,17 @@ def validate(config, valid_loader, model, criterion, epoch, cur_step):
             top1.update(accuracy["acc1"], bs)
             top5.update(accuracy["acc5"], bs)
 
-            if step % config.log_frequency == 0 or step == len(valid_loader) - 1:
[…]

### 2023-10-23 code/utils.py

@@ -70,7 +70,8 @@ class MyDartsTrainer(DartsTrainer):
                       "sepconv5x5": 4, "dilconv3x3" : 5, "dilconv5x5" : 6 } # индексы операций по названиям (в соответствии с nas_modules)
         O = len(operations) # кол-во операций
 
-        self.optimal = {} # выдает сглаженный тензор операций по названию операции
+        self.optimal_arc = {}
+
         with open(optimalPath) as f:
             checkpoint_optimum = json.load(f) # оптимальная архитектура в виде словаря
 
@@ -87,7 +88,7 @@ class MyDartsTrainer(DartsTrainer):
                 n = int(name[-8])
                 t = torch.zeros(n)
                 t[parents] = 1
-                self.optimal_arc[n] = t
+                self.optimal_arc[n] = t # 1 стоят там, где ребро есть, 0 там, где ребра нет
 
 
     def JSD(self):
@@ -127,17 +128,15 @@ class MyDartsTrainer(DartsTrainer):
         beta = {}
         for name, module in self.nas_modules:
             if name[-6:] == 'switch':
-                n = int(name[-8])
-                beta[n] = RelaxedOneHotCategorical(logits=module.alpha, temperature=self.t_beta).rsample().t()
+                n = int(name[-8]) # номер ноды
+                beta[n] = RelaxedOneHotCategorical(logits=module.alpha, temperature=self.t_beta).rsample().t() # записываем распределения по ребрам
 
-        for name, module in self.nas_modules: # суммируем диаергенцию по всем ребрам
+        for name, module in self.nas_modules: # разность по ребрам
             if name[-6:] != 'switch':
-                # print(F.softmax(module.alpha, dim=0), type(F.softmax(module.alpha, dim=0)))
                 alpha = RelaxedOneHotCategorical(logits=module.alpha, temperature=self.t_alpha).rsample().t()
                 alpha_opt = self.optimal_arc[name]
                 # alpha0 = RelaxedOneHotCategorical(probs=self.optimal[name], temperature=self.t).rsample().t()
-                # print(torch.dot(alpha, alpha0))
-                p, n = int(name[-1]), int(name[-4])
+                p, n = int(name[-1]), int(name[-4]) # номер parent и node
                 sum += torch.dot(alpha, alpha_opt) * beta[n][p] * self.optimal_arc[n][p]
         return sum
     
